---
title: "Output of functional enrichment result from metascape.org"
date: "2020.10.21"
output: pdf_document
    toc: true
---

## loading environment
```{r echo = FALSE, message = FALSE}
# devtools::install_github("hrbrmstr/ggalt")
library(ggplot2)
library(stringr)

library(ggalt)

theme_set(theme_classic())
meta_plot <- function(x, main) {
    names(x) <- c("term", "log10p", "observeRatio")
    x$term <- factor(x$term, levels = x$term[rev(order(x$log10p))])
    ggplot(x, aes(x = term, y = -log10p)) +
        geom_point(aes(, size = observeRatio * 100), stat = "identity") +
        geom_segment(aes(y = 0, x = term, yend = -log10p, xend = term), color = "black") +
        scale_x_discrete(labels = function(x) str_wrap(x, width = 60)) +
        labs(x = "", y = "-Log10(p)", size = "Observed ratio (%)", title = main) +
        theme(axis.text = element_text(color = "black", size = 12, hjust = 0,),
            axis.title = element_text(size = 12, face = "bold")) +
        coord_flip()
}
meta_plot_dumbbel <- function(x, main) {
    names(x) <- c("term", "log10p", "Enrichment", "Background")
    x$term <- factor(x$term, levels = x$term[order(x$Enrichment)])
    ggplot(x, aes(x = Background * 100, xend = Enrichment * 100, y = term, group = term)) +
        geom_dumbbell(color = "#e3e2e1", colour_x = "red", colour_xend = "blue", size = 2, dot_guide = TRUE, dot_guide_size = 0.25) +
        # geom_dumbbell(aes(size = -log10p), color = "#e3e2e1", colour_x = "red", colour_xend = "blue", dot_guide = TRUE, dot_guide_size = 0.25) + # used to present different P-value
        labs(y = "Functional category\n(p < 0.05)", x = "Proportion", title = main) +
        theme_bw() +
        theme(axis.text = element_text(color = "black", size = 10, hjust = 0,),
            axis.title = element_text(size = 10, face = "bold")) +
        theme(plot.margin = unit(c(1, 1, 1, 1), "cm")) +
        scale_color_manual(name = "", values = c("red", "blue"))
}
library(ggpubr)
library(egg) # for equal plot area
```

## 21.10.2020 Frist result
```{r eval = FALSE, echo = FALSE}
meta_inet_nonspecific <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/INET_nonspecific/metascape_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/inet_non_specific_meta.pdf", width = 10, height = 8)
meta_plot(meta_inet_nonspecific, "INET common targets")
dev.off()

meta_inet_specific <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/INET_specific/metascape_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/inet_specific_meta.pdf", width = 10, height = 8)
meta_plot(meta_inet_specific, "INET unique targets")
dev.off()

meta_y2h_nonspecific <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/Y2H_binary_common/metascape_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/Y2Hbinary_common_meta.pdf", width = 10, height = 8)
meta_plot(meta_y2h_nonspecific, "Y2H binary common targets")
dev.off()

meta_y2h_specific <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/Y2H_binary_unique/metascape_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/Y2Hbinary_unique_meta.pdf", width = 10, height = 8)
meta_plot(meta_y2h_specific, "Y2H binary unique targets")
dev.off()
```

## 25.10.2020 Second result
According to Fritz and Pascal, it makes less sense to separate unique and common proteins for functional enrichment assay.
***
The DisGeNET is used as another functional enrichment term for query.
> the DisGeNET terms with duplicated geneID were removed.

```{r eval = FALSE, echo = FALSE}
meta_inet_124 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/INET_all124_GO_reactome_KEGG/metascape_summary.csv", header = T)
disgenet_inet_124 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/INET_all124_GO_reactome_KEGG/Enrichment_QC/GO_DisGeNET_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/INET_all124_GO_reactome_KEGG_meta.pdf", width = 10, height = 9)
meta_plot(meta_inet_124, "Viral targeted human interactors (INET, n = 124)")
meta_plot_dumbbel(meta_inet_124, "INET")
meta_plot(disgenet_inet_124, "Gene-disease enrichment (INET, n = 124)")
dev.off()

meta_roth_229 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/Roth_all228_GO_reactome_KEGG/metascape_summary.csv", header = T)
disgenet_roth_229 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/Roth_all228_GO_reactome_KEGG/Enrichment_QC/GO_DisGeNET_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/Roth_all228_GO_reactome_KEGG_meta.pdf", width = 10, height = 8)
meta_plot(meta_roth_229, "Viral targeted human interactors (Roth, n = 229)")
meta_plot_dumbbel(meta_roth_229, "Roth")
meta_plot(disgenet_roth_229, "Gene-disease enrichment (Roth, n = 229)")
dev.off()

meta_y2h_346 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/2_Y2H_all346_GO_reactome_KEGG/metascape_summary.csv", header = T)
disgenet_y2h_346 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/meta_enrichment/2_Y2H_all346_GO_reactome_KEGG/Enrichment_QC/GO_DisGeNET_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/2_Y2H_all346_GO_reactome_KEGG_meta.pdf", width = 10, height = 9)
meta_plot(meta_y2h_346, "Viral targeted human interactors (binary, n = 346)")
meta_plot_dumbbel(meta_y2h_346, "Binary")
meta_plot(disgenet_y2h_346, "Gene-disease enrichment (binary, n = 346)")
dev.off()
```

## 09.11.2020 New INET interactome
```{r eval = FALSE, echo = FALSE}
binary_1107 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary/metascape_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/binary_GO_reactome_KEGG_meta.pdf", width = 15, height = 9)
# meta_plot(binary_1107, "Viral targeted human interactors (binary, n = 346)")
meta_plot_dumbbel(binary_1107, "Binary")
dev.off()
```

## 30.11.2020 Final integrate VirHostome

**2021.02.10** - update background list with HuRI_9.1 + fBFGORFeome

**2021.01.06** - update background list with hORFeome + fBFGORFeome

**2020.12.08** have figure with GO only

```{r}
# binary <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary/metascape_summary.csv", header = T)
# binary <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_GO_18232/metascape_summary.csv", header = T)
binary <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_GO_mergeORF/metascape_summary_20210212.csv", header = T)
names(binary) <- c("term", "-Log10(p)", "proportion", "background", "category", "enrichment")
binary$term <- factor(binary$term, levels = binary$term[order(binary$enrichment)])
# pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/binary_GO_reactome_KEGG_meta.pdf", width = 14, height = 9)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/binary_GO_merged2.pdf", width = 7, height = 5)
# meta_plot_dumbbel(binary, "VirHostome")
ggplot(binary, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity", fill = rgb(128, 41, 227, maxColorValue = 255)) +
    coord_flip() +
    labs(y = "Effect size", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold"))
dev.off()
```

## 05.12.2020 Functional enrichment analysis
**21.02.2021 21:18**- update Gordon data with the one from Science

1. Gordon AP-MS
```{r}
gordon <- read.csv("~/Documents/INET-work/virus_network/statistic_results/metascape/Gordon_Science_GO_customBG/metascape_summary.csv", header = T)
gordon$term <- factor(gordon$term, levels = gordon$term[order(gordon$enrichment)])
# pdf("~/Documents/INET-work/virus_network/figure_results/Gordon_GO_meta.pdf", width = 11, height = 9)
gordon_p <-
    ggplot(gordon, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity", fill = "black") +
    coord_flip() +
    labs(y = "Effect size", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold")) +
    theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
# dev.off()
```

2. Stukalov AP-MS
```{r}
Stukalov <- read.csv("~/Documents/INET-work/virus_network/statistic_results/metascape/Stukalov_GO_customBG/metascape_summary.csv", header = T)
Stukalov$term <- factor(Stukalov$term, levels = Stukalov$term[order(Stukalov$enrichment)])
# pdf("~/Documents/INET-work/virus_network/figure_results/Stukalov_GO_meta.pdf", width = 11, height = 9)
stukalov_p <-
    ggplot(Stukalov, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity", fill = "black") +
    coord_flip() +
    labs(y = "Effect size", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold")) +
    theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
# dev.off()
```

3. Li AP-MS
```{r}
Li <- read.csv("~/Documents/INET-work/virus_network/statistic_results/metascape/Li_GO_customBG/metascape_summary.csv", header = T)
Li$term <- factor(Li$term, levels = Li$term[order(Li$enrichment)])
# pdf("~/Documents/INET-work/virus_network/figure_results/Li_GO_meta.pdf", width = 11, height = 9)
li_p <-
    ggplot(Li, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity", fill = "black") +
    coord_flip() +
    labs(y = "Effect size", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold")) +
    theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
# dev.off()
```

4. Nabeel AP-MS
```{r}
Nabeel <- read.csv("~/Documents/INET-work/virus_network/statistic_results/metascape/Nabeel_GO_customBG/metascape_summary.csv", header = T)
Nabeel$term <- factor(Nabeel$term, levels = Nabeel$term[order(Nabeel$enrichment)])
# pdf("~/Documents/INET-work/virus_network/figure_results/Nabeel_GO_meta.pdf", width = 11, height = 9)
nabeel_p <-
    ggplot(Nabeel, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity", fill = "black") +
    coord_flip() +
    labs(y = "Effect size", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold")) +
    theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
# dev.off()
```

5. Merge 4 graphs into a single graphs
```{r}
pdf("~/Documents/INET-work/virus_network/figure_results/4interactom_GO_meta5.pdf", width = 10, height = 10)
ggarrange(gordon_p, stukalov_p, li_p, nabeel_p, ncol = 2, nrow = 2, labels = c("A", "B", "C", "D"))
dev.off()
```

## 16.12.2020 KEGG enrichment analysis for binary Y2H interactome
```{r}
kegg <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_KEGG/metascape_summary.csv", header = T)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/binary_KEGG_meta.pdf", width = 8, height = 4)
binary_kegg_p <- meta_plot_dumbbel(kegg, "Binary Y2H interactome")
binary_kegg_p
dev.off()
```

## 18.01.2021 viral protein, respectively
```{r}
N <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/N/metascape_summary.csv", header = T)
NSP6 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/NSP6/metascape_summary.csv", header = T)
NSP9 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/NSP9/metascape_summary.csv", header = T)
NSP12 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/NSP12/metascape_summary.csv", header = T)
NSP14 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/NSP14/metascape_summary.csv", header = T)
NSP16 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/NSP16/metascape_summary.csv", header = T)
ORF6 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/ORF6/metascape_summary.csv", header = T)
ORF7b <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/ORF7b/metascape_summary.csv", header = T)
ORF9c <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_viralProtein/ORF9c/metascape_summary.csv", header = T)
viral <- list(N = N, NSP6 = NSP6, NSP9 = NSP9, NSP12 = NSP12, NSP14 = NSP14, NSP16 = NSP16, ORF6 = ORF6, ORF7b = ORF7b, ORF9c = ORF9c)

for (i in 1:length(viral)) {
    graph <- meta_plot_dumbbel(viral[[i]], names(viral[i]))
    ggsave(paste0("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/binary_", names(viral[i]), "_Protein.pdf"), width = 10, height = 5)
}
```

## 04.05.2021 KEGG v2 and Reactome
```{r}
kegg_v2 <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/HuSCI_KEGG/metascape_summary.csv", header = T)
kegg_v2$term <- factor(kegg_v2$term, levels = kegg_v2$term[order(kegg_v2$enrichment)])
binary_kegg_p <-
    ggplot(kegg_v2, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(y = "Enrichment over background", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold")) +
    theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
ggsave(binary_kegg_p, file = "~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/HuSCI_KEGG_20210504.pdf", width = 6, height = 2)

reactome <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/HuSCI_reactome/metascape_summary.csv", header = T)
reactome$term <- factor(reactome$term, levels = reactome$term[order(reactome$enrichment)])
binary_reactome_p <-
    ggplot(reactome, aes(x = term, y = enrichment)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(y = "Enrichment over background", x = "Functional Category (p < 0.05)") +
    theme_bw() +
    theme(axis.text = element_text(color = "black", size = 8, hjust = 0),
        axis.title = element_text(size = 8, color = "black", face = "bold")) +
    theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
ggsave(binary_reactome_p, file = "~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/HuSCI_reactome_20210504.pdf", width = 6, height = 3)
```
