---
title: "Proportion of observed phosphoregulated proteins in VirHostome"
author: "Lin Chung-wen"
date: "1/13/2021, compiled at `r format(Sys.time(), '%d %m %y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# environment
```{r include = FALSE}
library(rethinking)
library(openxlsx)
source("~/Documents/Programming/R_functions/random_sig.r")
```

### search space and HuSCI binary interactions

<!-- - hORF: HORFeome_all.tsv -->
<!-- - fBFG: 20180927_bhORFeome_AD.xlsx -->
- merged: ORF_searchSpace.xlsx

```{r echo = FALSE}
# horf <- read.table("~/Documents/INET-work/references/HuRI_binaryPPI/HORFeome_all.tsv", header = T, sep = "\t")
# horf <- sort(horf$symbol)
# horf <- horf[!horf == "NULL"]

# fbfg <- read.xlsx("~/Documents/INET-work/references/HuRI_binaryPPI/20180927_bhORFeome_AD.xlsx")
# fbfg <- fbfg[-1, ]
# fbfg <- sort(unique(fbfg$X11))
# fbfg[1:21] <- c("MARCH1", "MARCH2", "MARCH3", "MARCH4", "MARCH5", "MARCH6", "MARCH7", "MARCH8", "MARCH9", "MARCH10", "SEP1", "SEP3", "SEP4", "SEP5", "SEP6", "SEP7", "SEP9", "SEP10", "SEP11", "SEP14", "DEC1")
# fbfg <- fbfg[!fbfg == "NULL"]
horf <- read.xlsx("~/Documents/INET-work/references/HuRI_binaryPPI/ORF_searchSpace.xlsx", sheet = 1)
horf_sym <- unique(horf$ensembl_geneName)
horf <- unique(horf$orf_id)

fbfg <- read.xlsx("~/Documents/INET-work/references/HuRI_binaryPPI/ORF_searchSpace.xlsx", sheet = 2)
fbfg_sym <- unique(fbfg$ensembl_geneName)
fbfg <- unique(fbfg$ORF_id)
tot_space <- unique(c(horf, fbfg))

total_sym <- unique(c(horf_sym, fbfg_sym))

binary <- read.xlsx("/Volumes/GoogleDrive/My Drive/Paper_VirHostome_CoV2/04_Supplementary Information/Supplementary_Table_1.xlsx", sheet = "1b - HuSCI", startRow = 4)
binary_human <- unique(binary$Host.protein_symbol)

huri <- read.csv("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_Tong_withSymbol.csv", header = T)
huri_uniq <- unique(c(huri$symbol_a, huri$symbol_b))

# dk <- read.xlsx("~/Google_lincw1111/VirHostome_CW/comparison/data/20201018_DK_VirHostome_Summary.xlsx", sheet = 1, startRow = 3)
```

## Two screening completeness comparison

```{r echo = FALSE}
paste0("fBFG-Y2H: ", length(fbfg))
paste0("classic Y2H (hORF): ", length(horf))
paste0("common ORF: ", table(horf %in% fbfg)[2])
paste0("all ORF: ", length(tot_space))
paste0("fBFG-Y2H viral ORF: ", 28)
paste0("classic viral ORF: ", 26)
paste0("fBFG search space: ", 28 * length(fbfg))
paste0("classic Y2H (hORF) search space, vPrey (AD), hBait (DB): ", 26 * 15236)
paste0("classic Y2H (hORF) search space, vPrey (DB), hBait (AD): ", 26 * length(horf))
paste0("common search space: ", 25 * table(horf %in% fbfg)[2])
paste0("total search space: ", 30 * length(tot_space))
paste0("Fraction of total: ", 100 * round((24 * table(horf %in% fbfg)[2])/(30 * length(tot_space)), 4), "%")
```

## viral prey-bait pairs
```{r}
viral <- read.xlsx("/Volumes/GoogleDrive/My Drive/Paper_VirHostome_CoV2/04_Supplementary Information/Supplementary_Table_1.xlsx", sheet = "1a - Viral ORFs", startRow = 4)
virals <- viral$Viral.protein[c(1:30)]
viral_his3 <- virals[viral$Y2HHIS3[!is.na(viral$Y2HHIS3)] == 1]
viral_gfp <- virals[viral$Y2HGFP[!is.na(viral$Y2HGFP)] == 1]

viral_overlap <- sum(viral_his3 %in% viral_gfp)^2 / length(unique(c(viral_his3, viral_gfp)))^2

print(paste("Y2HHIS3 viral preys:", length(viral_his3)))
print(paste("Y2HGFP viral preys:", length(viral_gfp)))
print(paste("Total pairs:", length(unique(c(viral_his3, viral_gfp))) ^ 2))
print(paste("Overlap:", (sum(viral_his3 %in% viral_gfp) ^ 2)  / (length(unique(c(viral_his3, viral_gfp))) ^ 2) * 100, "%"))
```

## observed phosphoregulated human targets
udpate with phosphoregulated gene list

```{r echo = FALSE}
# phos <- read.delim("~/Documents/INET-work/virus_network/references/04_Phosphoproteomics/Phosphoproteomics_Krogan/list.csv", header = T)
# phos <- phos$phosphoregulated
phos_bouhaddou <- read.xlsx("~/Documents/INET-work/virus_network/references/04_Phosphoproteomics/Phospho_Krogan.xlsx", sheet = 1)
phos_stukalov <- read.xlsx("~/Documents/INET-work/virus_network/references/04_Phosphoproteomics/Phospho_Pichlmair.xlsx", sheet = 1)
phos <- unique(c(phos_stukalov$Gene.symbol, phos_bouhaddou$Gene_Name))

binary_phos <- table(binary_human %in% phos)[2]
random_phos <- simula(10000, total_sym, binary_human, phos)
random_phos_huri <- simula(10000, huri_uniq, binary_human, phos)

# binary_phos_id <- binary_human[binary_human %in% phos]

paste("Observed phosphoregulated proteins within VirHostome:", binary_phos)
sign_phos <- round(1 - (abs(sig(as.numeric(random_phos), as.numeric(binary_phos))) / 10000), 4)
sign_phos_huri <- round(1 - (abs(sig(as.numeric(random_phos_huri), as.numeric(binary_phos))) / 10000), 4)
```

### Observed phosphoregulated proteins (VirHostome vs 10000 times random selection from combined ORF list).

```{r echo = FALSE, message = FALSE}
dens <- hist(random_phos, breaks = 39, plot = FALSE)
dens_huri <- hist(random_phos_huri, breaks = 39, plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_phosphoprotein2.pdf", width = 3, height = 3)
par(ps = 8, mar = c(4, 4, 5, 1))
# Human OFeome as BG
plot(dens, xlim = c(0, 50), col = "grey", freq = FALSE, border = NA, las = 1, xlab = "Number of phosphoregulated host proteins", ylab = "Frequency density", main = "HumanOFeome as background", xaxt = "n")
box(col = "black")
arrows(binary_phos, 150/10000, binary_phos, 10/10000, col = "red", lwd = 3, length = 0.1)
axis(side = 1, at = seq(1, 50, 5), labels = seq(1, 49, 5))
text(binary_phos, 200/10000, label = paste("p =", sign_phos), cex = 0.6)
# HuRI as BG
plot(dens_huri, xlim = c(0, 50), col = "grey", freq = FALSE, border = NA, las = 1, xlab = "Number of phosphoregulated host proteins", ylab = "Frequency density", main = "HuRI as background", xaxt = "n")
box(col = "black")
arrows(binary_phos, 150/10000, binary_phos, 10/10000, col = "red", lwd = 3, length = 0.1)
axis(side = 1, at = seq(1, 50, 5), labels = seq(1, 49, 5))
text(binary_phos, 200/10000, label = paste("p =", sign_phos_huri), cex = 0.6)
dev.off()
```

## observed ubiquitination
**2021.03.24 17:10**-
incorporate with IntAct binary data for ubiquitination protein assay
However, no idea how to perform the statistics assay with the data from IntAct.

**2021.03.24 21:11**-
Trying with HuRI 1st neighbor.

```{r}
# 1. compare between HuSCI and Ubiquitiome
ubiquit <- read.csv("~/Documents/INET-work/virus_network/references/PPIs/Stukalov_phosphoproteome_2020/ubituitination.csv", header = T)
ubiquit <- unique(ubiquit[ubiquit$sig == "Y", "first"])

binary_ubiq <- table(binary_human %in% ubiquit)[2]
# binary_ubiq_id <- binary_human[binary_human %in% ubiquit]
random_ubiq <- simula(10000, total_sym, binary_human, ubiquit)
sign_ubiq <- round(1 - (abs(sig(random_ubiq, binary_ubiq)) / 10000), 4)

paste("Observed ubiquitinated proteins within VirHostome:", binary_ubiq, "; p = ", sign_ubiq)

# 2. compare between HuSCI ubiquitination proteins in IntAct and Ubiquitiome
intact <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/HuSCI_IntAct_ubiquitination_list.csv", header = T)
intact_ubiq <- table(intact$name %in% ubiquit)[2]
# NOT correct here!
# random_intact_ubiq <- mcreplicate(10000, table(sample(total_sym, length(binary_human)) %in% ubiquit)[2], mc.cores = detectCores())

# 3. doing random rewiring
## original finding
### Ubiquitination proteins from HuSCI
binary_ubiq <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/HuSCI_and_HuRI.csv", header = T)
binary_ubiq <- unique(binary_ubiq[binary_ubiq$ubiquitin == 1, "name"]) # 30 proteins from HuSCI
binary_ubiq <- binary_ubiq[!is.na(binary_ubiq)]

### 1st neighbor of Ubiquitination proteins and how many of them are in Ubiquitiome
library(igraph)
huri <- read.csv("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_Tong_withSymbol.csv", header = T)
huri <- huri[, c(5:6)]
graph <- graph_from_data_frame(huri, directed = FALSE)
graph <- simplify(graph, remove.loops = FALSE)
binary_ubiq_subnet <- ego(graph, order = 1, nodes = binary_ubiq[c(1:28, 30)], mode = "all") # "UGGT2" not found in HuRI
binary_ubiq_1st <- unique(names(unlist(binary_ubiq_subnet))) # 1st neighbors of 30 proteins from HuSCI
binary_ubiq_check <- as.numeric(table(unique(names(unlist(binary_ubiq_subnet))) %in% ubiquit)[2]) # 1st neighbors of 30 proteins from HuSCI in Ubiquitiome

## network rewiring
rewire_output <- function(x) {
    rewired_graph <- simplify(rewire(graph, keeping_degseq(niter = gsize(graph) * 10)), remove.loops = FALSE)
    binary_rewire_subnet <- ego(rewired_graph, order = 1, nodes = binary_ubiq[c(1:28, 30)], mode = "all") # "UGGT2" not found in HuRI
    binary_rewire_check <- as.numeric(table(unique(names(unlist(binary_rewire_subnet))) %in% ubiquit)[2])
    return(binary_rewire_check)
}
random_intact_ubiq <- mcreplicate(10000, rewire_output(), mc.cores = detectCores())
sign_intact_ubiq <- round(1 - (abs(sig(random_intact_ubiq, binary_ubiq_check)) / 10000), 4)
paste("Observed ubiquitinated proteins within 1st neighbor:", binary_ubiq_check, "; p = ", sign_intact_ubiq)
```

### Observed ubiquitinated proteins (VirHostome vs 10000 times random selection from combined ORF list).
**2021.03.25 00:00**-
have graph for 1st random simulation

```{r echo = FALSE, message = FALSE}
dens <- hist(random_ubiq, plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_ubiquitination.pdf", width = 3, height = 3)
par(ps = 8)
plot(dens, xlim = c(0, 50), col = "grey", freq = FALSE, border = NA, las = 1, xlab = "Number of ubiquitinated host proteins", ylab = "Frequency density", main = NULL)
box(col = "black")
arrows(binary_ubiq, 400/10000, binary_ubiq, 10/10000, col = "red", lwd = 2)
text(binary_ubiq - 1, 550/10000, label = paste("p =", sign_ubiq), cex = 0.6)
dev.off()

dens <- hist(random_intact_ubiq, plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_1stNB_ubiquitination.pdf", width = 3, height = 3)
par(ps = 8)
plot(dens, xlim = c(0, 100), col = "grey", freq = FALSE, border = NA, las = 1, xlab = "Number of ubiquitinated human proteins", ylab = "Frequency density", main = NULL)
box(col = "black")
arrows(binary_ubiq_check, 100/10000, binary_ubiq_check, 10/10000, col = "red", lwd = 2, length = 0.1)
text(binary_ubiq_check - 1, 150/10000, label = paste("p =", sign_intact_ubiq), cex = 0.6)
dev.off()
```

## observed RNA binding protein (RBP)
**2021.03.23 12:42**-

```{r}
RBP8 <- read.xlsx("~/Documents/INET-work/virus_network/references/protein_RNA/media-1.xlsx", sheet = 1)
RBP24 <- read.xlsx("~/Documents/INET-work/virus_network/references/protein_RNA/media-1.xlsx", sheet = 2)
RBP8_sig <- RBP8[!is.na(RBP8[RBP8$logFC >= 1 | RBP8$logFC <= -1, "Gene.name"]), "Gene.name"]
RBP8_sig <- RBP8_sig[!is.na(RBP8_sig)]

RBP24$adj.P.Val[is.na(RBP24$adj.P.Val)] <- 1 # necessary because NA will also be included
RBP24_sig <- RBP24[RBP24$adj.P.Val < 0.1, "Gene.name"]
RBP24_sig <- RBP24_sig[c(1:330)]

binary_rbp <- table(binary_human %in% RBP8$Gene.name)[2] # cRIC
random_rbp <- simula(10000, total_sym, binary_human, RBP8$Gene.name) # cRIC
random_rbp_huri <- simula(10000, huri_uniq, binary_human, RBP8$Gene.name) # cRIC

# paste("Observed RNA binding proteins within VirHostome:", binary_rbp)
sign_rbp <- round(1 - (abs(sig(random_rbp, binary_rbp)) / 10000), 4) # cRIC
sign_rbp_huri <- round(1 - (abs(sig(random_rbp_huri, binary_rbp)) / 10000), 4) # cRIC

# 2021.04.11 **12:00pm**
# cRIC significant
binary_rbp24 <- table(binary_human %in% RBP24_sig)[2]
random_rbp24 <- simula(10000, total_sym, binary_human, RBP24_sig)
sign_rbp24 <- round(1 - (abs(sig(random_rbp24, binary_rbp24)) / 10000), 4)
random_rbp24_huri <- simula(10000, huri_uniq, binary_human, RBP24_sig)
sign_rbp24_huri <- round(1 - (abs(sig(random_rbp24_huri, binary_rbp24)) / 10000), 4)

# 2021.03.23 12:44
RBP_vRIC <- read.xlsx("~/Documents/INET-work/virus_network/references/protein_RNA/media-5.xlsx", sheet = 1)
RBP_vRIC <- RBP_vRIC[RBP_vRIC$logFC > 0, ] # all
RBP_vRIC2 <- RBP_vRIC[RBP_vRIC$Sig.vRNA.Interactors.FDR10 == "Yes", ] # significant

binary_rbpvric <- table(binary_human %in% RBP_vRIC$Gene.name)[2]
# binary_rbpvric_id <- binary_human[binary_human %in% RBP_vRIC$Gene.name]
random_rbpvric <- simula(10000, total_sym, binary_human, RBP_vRIC$Gene.name)
sign_rbpvric <- round(1 - (abs(sig(random_rbpvric, binary_rbpvric)) / 10000), 4)
random_rbpvric_huri <- simula(10000, huri_uniq, binary_human, RBP_vRIC$Gene.name)
sign_rbpvric_huri <- round(1 - (abs(sig(random_rbpvric_huri, binary_rbpvric)) / 10000), 4)
# vRIC significant
binary_rbpvric2 <- table(binary_human %in% RBP_vRIC2$Gene.name)[2]
random_rbpvric2 <- simula(10000, total_sym, binary_human, RBP_vRIC2$Gene.name)
sign_rbpvric2 <- round(1 - (abs(sig(random_rbpvric2, binary_rbpvric2)) / 10000), 4)
random_rbpvric2_huri <- simula(10000, huri_uniq, binary_human, RBP_vRIC2$Gene.name)
sign_rbpvric2_huri <- round(1 - (abs(sig(random_rbpvric2_huri, binary_rbpvric2)) / 10000), 4)
```

### Observed RNA binding proteins (VirHostome vs 10000 times random selection from combined ORF list).

```{r echo = FALSE, message = FALSE}
# cRIC
dens <- hist(random_rbp, breaks = 20, plot = FALSE)
dens_huri <- hist(random_rbp_huri, breaks = 20, plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_RBPcRIC.pdf", width = 3, height = 3)
par(mgp = c(2, 0.7, 0), ps = 8)
plot(dens, xlim = c(0, 20), ylim = c(0, 0.17), col = rgb(0.75, 0.75, 0.75, 1/2), freq = FALSE, border = NA, las = 1, xlab = "Number of identified RBP", ylab = "Frequency density", main = "from cRIC\n(all)", xaxt = "n")
plot(dens_huri, xlim = c(0, 20), col = rgb(1, 0.65, 0, 1/2), freq = FALSE, border = NA, las = 1, xlab = "Number of identified RBP", ylab = "Frequency density", xaxt = "n", add = T)
axis(side = 1, at = seq(1, 20, 4) - 0.5, labels = seq(0, 19, 4))
box(col = "black")
arrows(binary_rbp + 0.5, 400/10000, binary_rbp + 0.5, 10/10000, col = "red", lwd = 2, length = 0.1)
text(binary_rbp - 4, 550/10000, paste0("p = ", sign_rbp, "(integrate search space)\np = ", sign_rbp_huri, " (HuRI)"), cex = 0.4, pos = 4)
legend(9, 0.17, inset = 0.02, legend = c("Integrated search space", "HuRI"), fill = c(rgb(0.75, 0.75, 0.75, 1/2), rgb(1, 0.65, 0, 1/2)), cex = 0.5, bty = "n")

# 2021.04.11 **12:13pm**
# cRIC significant
dens <- hist(random_rbp24, breaks = 13, plot = FALSE)
dens_huri <- hist(random_rbp24_huri, breaks = 13, plot = FALSE)
plot(dens, xlim = c(0, 15), col = rgb(0.75, 0.75, 0.75, 1/2), freq = FALSE, border = NA, las = 1, xlab = "Number of identified RBP", ylab = "Frequency density", main = "from cRIC\n(adj.p < 0.1)", xaxt = "n")
plot(dens_huri, xlim = c(0, 15), col = rgb(1, 0.65, 0, 1/2), freq = FALSE, border = NA, las = 1, xaxt = "n", add = T)
axis(side = 1, at = c(seq(1, 15, 3) - 0.5, 15), labels = seq(0, 15, 3))
box(col = "black")
arrows(binary_rbp24 + 0.5, 400/10000, binary_rbp24 + 0.5, 10/10000, col = "red", lwd = 2, length = 0.1)
text(binary_rbp24, 550/10000, label = paste0("p = ", sign_rbp24, "(integrate search space)\np = ", sign_rbp24_huri, " (HuRI)"), cex = 0.4, pos = 4)
legend(5, 0.2, inset = 0.02, legend = c("Integrated search space", "HuRI"), fill = c(rgb(0.75, 0.75, 0.75, 1/2), rgb(1, 0.65, 0, 1/2)), cex = 0.5, bty = "n")
dev.off()

# 2021.03.23 12:44
# vRIC
dens <- hist(random_rbpvric, breaks = 12, plot = FALSE)
dens_huri <- hist(random_rbpvric_huri, breaks = 12, plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_RBPvRIC.pdf", width = 3, height = 3)
par(mgp = c(2, 0.7, 0), ps = 8)
plot(dens, xlim = c(0, 15), col = rgb(0.75, 0.75, 0.75, 1/2), freq = FALSE, border = NA, las = 1, xlab = "Number of identified RBP", ylab = "Frequency density", main = "from vRIC RBP list\n(all, logFC > 0)", xaxt = "n")
plot(dens_huri, xlim = c(0, 15), col = rgb(1, 0.65, 0, 1/2), freq = FALSE, border = NA, las = 1, xaxt = "n", add = T)
axis(side = 1, at = c(seq(1, 15, 3) - 0.5, 15), labels = seq(0, 15, 3))
box(col = "black")
arrows(binary_rbpvric + 0.5, 400/10000, binary_rbpvric + 0.5, 10/10000, col = "red", lwd = 2, length = 0.1)
text(binary_rbpvric - 4, 550/10000, label = paste0("p = ", sign_rbpvric, "(integrate search space)\np = ", sign_rbpvric_huri, " (HuRI)"), cex = 0.4, pos = 4)
legend(5, 0.2, inset = 0.02, legend = c("Integrated search space", "HuRI"), fill = c(rgb(0.75, 0.75, 0.75, 1/2), rgb(1, 0.65, 0, 1/2)), cex = 0.5, bty = "n")
# sig one
dens <- hist(random_rbpvric2, breaks = 8, plot = FALSE)
dens_huri <- hist(random_rbpvric2_huri, breaks = 7, plot = FALSE)
plot(dens, xlim = c(0, 10), col = rgb(0.75, 0.75, 0.75, 1/2), freq = FALSE, border = NA, las = 1, xlab = "Number of identified RBP", ylab = "Frequency density", main = "from vRIC RBP list\n(adj.p < 0.1, logFC > 0)", xaxt = "n")
plot(dens_huri, xlim = c(0, 10), col = rgb(1, 0.65, 0, 1/2), freq = FALSE, border = NA, las = 1, xaxt = "n", add = T)
axis(side = 1, at = c(seq(1, 8, 2) - 0.5, 9), labels = seq(0, 8, 2))
box(col = "black")
arrows(binary_rbpvric2 + 0.5, 1000/10000, binary_rbpvric2 + 0.5, 100/10000, col = "red", lwd = 2, length = 0.1)
text(binary_rbpvric2, 1550/10000, paste0("p = ", sign_rbpvric2, "(integrate search space)\np = ", sign_rbpvric2_huri, " (HuRI)"), cex = 0.4, pos = 4)
legend(4, 0.5, inset = 0.02, legend = c("Integrated search space", "HuRI"), fill = c(rgb(0.75, 0.75, 0.75, 1/2), rgb(1, 0.65, 0, 1/2)), cex = 0.5, bty = "n")
dev.off()
```

## Comparison with previously identified viral targets
~~NOT NECESSARY NOW~~
**22.02.2021 09:37**- included in VirHostome paper now

```{r}
previous <- read.xlsx("~/Documents/INET-work/virus_network/references/Interaction\ Counts\ Per\ Human\ Protein\ wo\ spoke,\ wo\ prot-RNA.xlsx")
previous <- unique(previous$unique)

binary_pre <- table(binary_human %in% previous)[2]

random_pre <- mcreplicate(10000, table(sample(total_sym, length(binary_human)) %in% previous)[2], mc.cores = detectCores())

paste("Observed in previous identified human target within VirHostome:", binary_pre)
sign_pre <- round(1 - (abs(sig(as.numeric(random_pre), as.numeric(binary_pre))) / 10000), 4)
```

### Observed human proteins in previous identified targets (VirHostome vs 10000 times random selection from combined ORF list).

```{r echo = FALSE, message = FALSE}
dens <- hist(random_pre, breaks = seq(0, 50, by = 2), plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_preIdentified.pdf", width = 3, height = 3)
par(ps = 8)
plot(dens, xlim = c(0, 70), freq = FALSE, col = "grey", border = NA, las = 1, xlab = "Number of previous known viral targets", ylab = "Frequency density", main = NULL)
box(col = "black")
arrows(binary_pre, 400/10000, binary_pre, 10/10000, col = "red", lwd = 2)
text(binary_pre - 1, 550/10000, label = paste("p =", sign_pre), cex = 0.6)
dev.off()
```

## Comparison with intra-viral interactome

```{r}
library(igraph)
sars2 <- read.xlsx("~/Google_lincw1111/VirHostome_CW/cloning/data/SARS2_seq_supplementary.xlsx")
sars2$"viral.protein"[c(11, 12)] <- "NSP12"
sars2 <- toupper(unique(sars2$"viral.protein"))

y2h_intra <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/intraviral_edge.csv", header = T)
y2h_intra <- data.frame(vAD = toupper(y2h_intra$vAD), vDB = toupper(y2h_intra$vDB))
y2h_graph <- graph_from_data_frame(y2h_intra)
y2h_intra <- unique(c(toupper(y2h_intra$vAD), toupper(y2h_intra$vDB)))

intra_viral <- read.csv("~/Documents/INET-work/virus_network/references/PPIs/Li_virus-host/Y2H_list.csv", header = T)
intra_graph <- graph_from_data_frame(intra_viral)
intra_viral <- unique(c(intra_viral$FROM, intra_viral$TO))

binary_intra <- gsize(intersection(intra_graph, y2h_graph))

sars2_rep <- function(x) {
  sars2_sample <- data.frame(from = sample(x, 27, replace = TRUE), to = sample(x, 27, replace = TRUE))
  sars2_sample_graph <- simplify(graph_from_data_frame(sars2_sample))
  return(gsize(intersection(intra_graph, sars2_sample_graph)))
}

random_intra <- mcreplicate(10000, sars2_rep(sars2), mc.cores = detectCores())

paste("Observed in intra_viral identified human target within VirHostome:", binary_intra)
sign_intra <- round(1 - (abs(sig(as.numeric(random_intra), as.numeric(binary_intra))) / 10000), 4)
```

### Observed intra-viral interactome (VirHostome vs 10000 times random selection from combined ORF list).

```{r echo = FALSE, message = FALSE}
dens <- hist(random_intra, breaks = 5, plot = FALSE)
pdf("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/random_intraViral.pdf", width = 3, height = 3)
par(ps = 8)
plot(dens, xlim = c(0, 6), freq = FALSE, col = "grey", border = NA, las = 1, xlab = "Number of PPI in intraviral interactome", ylab = "Frequency density", main = NULL)
box(col = "black")
arrows(binary_intra, 1000/10000, binary_intra, 10/10000, col = "red", lwd = 2)
text(binary_intra - 1, 550/10000, label = paste("p =", sign_intra), cex = 0.6)
dev.off()
```
