---
title: "extract VirHostome subnetwork from HuRI network"
date: "2020.11.02, last compiled on `r format(Sys.time(), "%d %b, %Y")`"
output:
  html_document:
    toc: true
    toc_depth: 2
---
## history
**2021.01.28 15:25** - have new network graph with categorized term

**2020.11.26 23:50**

Have the SARS-CoV-2 interaction pairs from DK.

**2020.11.19**

The SARS-CoV-2-human interactome from INET was updated, not yet from Roth.

**2020.11.07**

Applying the updated INET viral-host interaction network infomation.
It is because both directors agree to combine two Y2H networks, the following assay is majorly based on the binary version.

**2020.11.06**

According to Dan-Kyun (DK) and Pascal, the HuRI contains 3 different assays, each of them was using different clone construction.
Current INET VirHostome is using the same clone strategy as HuRI assay 1 and 2, Roth VirHostome is using the strategy as assay 3.

**2020.11.02**

Proteins in biology used to work together for specific purpose. The community network presents the possible interacted proteins.

  > However, the list from Tong seems slightly different from the supplementary file of HuRI published on Nature! Waiting for response.

## working environment
```{r echo = FALSE, message = FALSE2}
# knitr::opts_knit$set(root.dir = normalizePath("~/Documents/INET-work/virus_network/Y2H_screening/20200923_verified/"))
library(RColorBrewer)
library(reshape2)
library(igraph)
network_plot <- function(subnetwork, main) {
    plot(subnetwork, layout = layout_in_circle, vertex.size = 4, vertex.label = NA, edge.arrow.size = 0.5)
    text(1, 1.2, paste0(main, " human-human \ninteraction subnetwork"), pos = 4)
    text(1.1, 0.9, paste0("Node: ", length(V(subnetwork)), "\n", "Edge: ", length(E(subnetwork))), col = "darkblue", pos = 4)
}

library(linkcomm) # using edge similarity to reveal community

library(RCy3) # interact with cytoscape, for better visualization

library(gridExtra) # display table information into a bar plot
library(grid)
```

## loading data
```{r}
huri <- read.csv("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_Tong_withSymbol.csv", header = T)
huri <- huri[, c(5:6)]
binary_ori <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/binary_node_1126.csv", header = T)
binary_edge <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/binary_edge_1126.csv", header = T)

hi <- read.table("~/Documents/INET-work/references/HuRI_binaryPPI/HI-union.txt", header = F, sep = "\t")
```

## create binary network
```{r}
# viral-host network
binary_graph <- graph_from_data_frame(binary_edge, directed = FALSE)
V(binary_graph)$group <- binary_ori[match(names(V(binary_graph)), binary_ori$node), "group"]

# subnetwork from HuRI
graph <- graph_from_data_frame(huri, directed = FALSE)
graph <- simplify(graph, remove.loops = FALSE)
binary <- unique(binary_ori[binary_ori$node %in% names(V(graph)), "node"])

binary_sub_graph <- induced_subgraph(graph, binary)
binary_sub_graph <- simplify(binary_sub_graph, remove.loops = FALSE)
# merge viral-host network and HuRI subnetwork
binary_merge <- union(binary_graph, binary_sub_graph)

# HI-union
hi_graph <- simplify(graph_from_data_frame(hi, directed = FALSE), remove.loops = FALSE)

# subnetwork from HI
binary_hi <- unique(binary_ori[binary_ori$node %in% names(V(hi_graph)), "node"])
binary_hi_sub_graph <- induced_subgraph(hi_graph, binary_hi)
binary_hi_sub_graph <- simplify(binary_hi_sub_graph, remove.loops = FALSE)
# merge viral-host network and HI subnetwork
binary_hi_merge <- union(binary_graph, binary_hi_sub_graph)
```

## output human-human subnetwork
```{r eval = FALSE, echo = FALSE}
# NOT RUN FOR FINAL
write.table(as_data_frame(inet_sub_graph), file = "inet_huri_sub_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
write.table(as_data_frame(roth_sub_graph), file = "roth_huri_sub_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
write.table(as_data_frame(binary_sub_graph), file = "binary_huri_sub_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
```

## ploting the network in circle layout
```{r eval = FALSE, echo = FALSE}
# INET
network_plot(inet_sub_graph, "INET")
text(-1.7, 1.2, "INET SARS-CoV-2 \nVirHostome", pos = 4)
text(-1, 0.9, paste0("Node: ", length(V(inet_graph)), "\n", "Edge: ", length(E(inet_graph))), col = "darkblue", pos = 2)
network_plot(inet_merge, "Union INET")

# Roth
network_plot(roth_sub_graph, "Roth")
text(-1.7, 1.2, "Roth SARS-CoV-2 \nVirHostome", pos = 4)
text(-1, 0.9, paste0("Node: ", length(V(roth_graph)), "\n", "Edge: ", length(E(roth_graph))), col = "darkblue", pos = 2)
network_plot(roth_merge, "Union Roth")

# INET + Roth
network_plot(binary_sub_graph, "Binary")
text(-1.7, 1.2, "Binary SARS-CoV-2 \nVirHostome", pos = 4)
text(-1, 0.9, paste0("Node: ", length(V(binary_graph)), "\n", "Edge: ", length(E(binary_graph))), col = "darkblue", pos = 2)
network_plot(binary_merge, "Union Binary")
```

### color and layout information
```{r message = FALSE}
pal <- brewer.pal(length(unique(V(binary_graph)$group)), "Dark2")
red_blue <- c("#56BCF9", "#EA3323")
col11 <- c('#e6194b', '#3cb44b', '#ffe119', '#4363d8', '#f58231', '#911eb4', '#46f0f0', '#f032e6', '#bcf60c', '#fabebe', '#008080', '#e6beff', '#9a6324', '#fffac8', '#800000', '#aaffc3', '#808000', '#ffd8b1', '#000075', '#808080', '#ffffff', '#000000')
l <- layout.fruchterman.reingold(binary_merge, niter = 10000, area = vcount(binary_merge)^4*10)
# l <- layout_nicely(binary_merge)
```
## plot the network in auto layout
### binary viral-host interactome
```{r eval = FALSE, echo = FALSE, message = FALSE}
l <- layout_with_dh
## plot with different vertex annotation
pdf("/tmp/binary_virhostome.pdf", width = 8, height = 5)
par(mar = c(0, 0, 0, 0) + 3)
plot(binary_graph, vertex.color = red_blue[as.numeric(as.factor(vertex_attr(binary_graph, "group")))], vertex.size = 2, vertex.label.cex = .5, vertex.label.dist  = 0.9, vertex.label.color = "black", asp = 0.5, margin = 0, layout = l)
legend(x = -1, y = -1, c("Binary target", "viral-protein"), pch = 21, col = "#777777", pt.bg = red_blue, pt.cex = 1, cex = .5, bty = "n", ncol = 1)
text(x = -1, y = 1, labels = paste0("node: ", length(V(binary_graph))), col = "black", cex = .5, adj = NULL, pos = NULL)
text(x = -0.9, y = 0.9, labels = paste0("- viral protein: ", sum(V(binary_graph)$group == "virus")), col = "black", cex = .5, adj = NULL, pos = NULL)
text(x = -0.88, y = 0.8, labels = paste0("- human target: ", sum(V(binary_graph)$group == "human")), col = "black", cex = .5, adj = NULL, pos = NULL)

text(x = -1, y = 0.7, labels = paste0("edge: ", length(E(binary_graph))), col = "black", cex = .5, adj = NULL, pos = NULL)
dev.off()
```

### binary viral-host-host interactome
```{r eval = FALSE, echo = FALSE}
pdf("/tmp/binary_virhostome_mitHuRI.pdf", width = 8, height = 5)
plot(binary_merge, vertex.color = pal[as.numeric(as.factor(vertex_attr(binary_graph, "group")))], vertex.size = 3, vertex.label.cex = .3, vertex.label.color = "black", vertex.label = NA, asp = 0, margin = 0)
legend(x = -1, y = -1, c("Binary target", "INET target", "Roth target", "viral-protein"), pch = 21, col = "#777777", pt.bg = pal, pt.cex = 1, cex = .5, bty = "n", ncol = 1)
dev.off()
```

## output merged network
```{r eval = FALSE, echo = FALSE}
# NOT RUN FOR FINAL
write.table(as_data_frame(inet_merge), file = "inet_merged_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
write.table(as_data_frame(roth_merge), file = "roth_merged_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
write.table(as_data_frame(binary_merge), file = "binary_merged_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
write.table(as_data_frame(binary_graph), file = "binary_edge.csv", sep = ",", row.names = FALSE, quote = FALSE)
write.table(as_data_frame(binary_graph, what = "vertices"), file = "binary_node.csv", sep = ",", row.names = FALSE, quote = FALSE)
```

## doing community calculation
based on merged binary interaction network
```{r eval = FALSE, echo = FALSE}
# Community structure detection based on edge betweenness
ceb <- cluster_edge_betweenness(binary_merge, directed = FALSE)

# Community strucure via short random walks
cw <- cluster_walktrap(binary_merge)

# Community structure via greedy optimization of modularity
cfg <- cluster_fast_greedy(simplify(binary_merge))

# propagating labels
clp <- cluster_label_prop(binary_merge)

# Community structure detecting based on the leading eigenvector of the community matrix
cle <- cluster_leading_eigen(binary_merge)

# Finding community structure by multi-level optimization of modularity
cl <- cluster_louvain(binary_merge)

par(mfrow = c(2, 3))
barplot(sizes(ceb), main = "ceb", xlab = "community", ylab = "size", las = 1)
barplot(sizes(cw), main = "cw", xlab = "community", ylab = "size", las = 1)
barplot(sizes(cfg), main = "cfg", xlab = "community", ylab = "size", las = 1)
barplot(sizes(clp), main = "clp", xlab = "community", ylab = "size", las = 1)
barplot(sizes(cle), main = "cle", xlab = "community", ylab = "size", las = 1)
barplot(sizes(cl), main = "cl", xlab = "community", ylab = "size", las = 1)
```
```{r eval = FALSe, echo = FALSE}
coords <- l[match(ceb[[1]], names(V(binary_merge))), ]
g1 <- induced_subgraph(binary_merge, V(binary_merge)[ceb[[1]]])
barcolor <- colorRampPalette(brewer.pal(11, "Spectral"))
pdf("/tmp/binary_virhostome_mitHuRI_community_bar.pdf", width = 8, height = 5)
par(mar = c(5, 5, 2, 2))
barplot(sizes(ceb), xlab = "community", ylab = "size", las = 1, col = barcolor(length(ceb)))
dev.off()
pdf("/tmp/binary_virhostome_mitHuRI_community_original.pdf", width = 8, height = 5)
par(mar = c(-1, 0, -3, 1) + 3)
plot(binary_merge, layout = l, vertex.color = pal[as.numeric(as.factor(vertex_attr(binary_graph, "group")))], vertex.size = 3, vertex.label.cex = .3, vertex.label.color = "black", vertex.label = NA, asp = 0, margin = 0)
legend(x = -1, y = -1, c("Binary target", "INET target", "Roth target", "viral-protein"), pch = 21, col = "#777777", pt.bg = pal, pt.cex = 1, cex = .5, bty = "n", ncol = 1)
dev.off()
pdf("/tmp/binary_virhostome_mitHuRI_community.pdf", width = 8, height = 5)
par(mar = c(-1, 0, -3, 1) + 3)
plot(ceb, binary_merge, layout = l, vertex.color = pal[as.numeric(as.factor(vertex_attr(binary_graph, "group")))], vertex.size = 3, vertex.label.cex = .3, vertex.label.color = "black", vertex.label = NA, asp = 0, margin = 0)
dev.off()
```

### have individual clusters and output community established according to edge-betweenness
```{r eval = FALSE, echo = FALSE}
ceb_tb <- membership(ceb)
ceb_df <- as.data.frame(matrix(ceb_tb))
names(ceb_df) <- "community"
ceb_df$gene <- names(ceb_tb)
ceb_df$group <- ifelse(ceb_df$gene %in% names(V(inet_graph)), ifelse(ceb_df$gene %in% names(V(roth_graph)), "binary", "inet"), "roth")
ceb_df$group <- ifelse(ceb_df$gene %in% virus, "viral", ceb_df$group)
ceb_df <- ceb_df[order(ceb_df$community, ceb_df$group), ]
write.table(ceb_df, file = "/tmp/ceb_df.csv", sep = ",", row.names = FALSE)

ceb_c2 <- induced_subgraph(binary_merge, names(ceb_tb[ceb_tb == 2]))
ceb_c5 <- induced_subgraph(binary_merge, names(ceb_tb[ceb_tb == 5]))
pdf("/tmp/binary_virhostome_mitHuRI_cluster2.pdf", width = 5, height = 4)
plot(ceb_c2, vertex.color = pal[as.numeric(as.factor(vertex_attr(binary_graph, "group")))], vertex.size = 3, vertex.label.cex = .3, vertex.label.color = "black", vertex.label = NA, asp = 0, margin = 0)
title("Community 2, NSP16")
legend(x = -1, y = -1, c("Binary target", "INET target", "Roth target", "viral-protein"), pch = 21, col = "#777777", pt.bg = pal, pt.cex = 1, cex = .5, bty = "n", ncol = 1)
dev.off()
pdf("/tmp/binary_virhostome_mitHuRI_cluster5.pdf", width = 5, height = 4)
plot(ceb_c5, vertex.color = pal[as.numeric(as.factor(vertex_attr(binary_graph, "group")))], vertex.size = 3, vertex.label.cex = .3, vertex.label.color = "black", vertex.label = NA, asp = 0, margin = 0)
title("Community 5, NSP14")
legend(x = -1, y = -1, c("Binary target", "INET target", "Roth target", "viral-protein"), pch = 21, col = "#777777", pt.bg = pal, pt.cex = 1, cex = .5, bty = "n", ncol = 1)
dev.off()
```

## doing network community assay, based on edge similarity (link community)
```{r eval = FALSE, echo = FALSE}
# based on edge similarity, only analyze viral-host-host network
binary_df <- unique(as_data_frame(binary_merge))
lc <- getLinkCommunities(binary_df)
lc_clusters <- lengths(lc$clusters)
lc_df_edges <- as.data.frame(lc$edges)
lc_df_edges$sharename <- paste0(lc_df_edges$node1, " (interacts with) ", lc_df_edges$node2)
lc_df_edgelist <- as.data.frame(lc$edgelist)
lc_df_edgelist$sharename <- paste0(lc_df_edgelist$V1, " (interacts with) ", lc_df_edgelist$V2)
lc_df_edgelist$cluster <- lc_df_edges[match(lc_df_edgelist$sharename, lc_df_edges$sharename), "cluster"]
names(lc_clusters) <- c(1:length(lc_clusters))
pdf("/tmp/binary_virhostome_mitHuRI_linkcomm_members.pdf", width = 8, height = 5)
barplot(lc_clusters, xlab = "community", ylab = "size", las = 1, col = barcolor(length(lc_clusters)))
dev.off()
pdf("/tmp/binary_virhostome_mitHuRI_linkcomm.pdf", width = 5, height = 5)
par(mar = c(0, 0, 0, 0))
plot(lc, type = "graph", layout = layout.kamada.kawai, shownodesin = 20)
dev.off()
pdf("/tmp/binary_virhostome_mitHuRI_linkcomm_clusters.pdf", width = 8, height = 5)
plot(lc, type = "graph", vsize = 5, vlabel = F, clusterids = c(9, 26, 34, 45, 50, 61))
# title("Edge similarity community 9/26/34/45/50/61")
dev.off()

## output edge similarity community
write.table(lc_df_edgelist, file = "~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/binary_linkcomm_edge_community.csv", sep = ",", row.names = FALSE)
```

## 2020.11.11 check community in HuRI
**16:00** - not finished yet
```{r}
graph_ceb <- cluster_edge_betweenness(graph, directed = FALSE)

```

## 2020.11.12 merge functional category into binary viral-host-host network
It is always better able to corperate with a visualization tool, therefore the *RCy3* package is used here.

**2020.11.27 00:17** - using metascape summary from binary interactome dataset.
```{bash eval = FALSE, echo = FALSE}
perl $HOME/Documents/INET-work/INETscripts/print_meta.pl GO_proteinList.txt > metascape_GOnetwork.tsv
```

**Create co-occurence-matrix** -
  > https://stackoverflow.com/questions/13281303/creating-co-occurrence-matrix

### 2021.01.28 14:53 - update network graph with merged functional category

**11.13 14:31** - having gene-disease information from GWAS catelog and GWAS database
```{r}
# enriched functional categories of binary network
fb_edge <- read.table("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_GO_mergeORF/metascape_mergeTermNetwork_20210212.csv", sep = ",", header = T)
fb_node_ori <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary_GO_mergeORF/metascape_mergeTermNode_20210212.csv", sep = ",", header = T)
fb_node <- fb_node_ori
fb_graph <- simplify(graph_from_data_frame(fb_edge, directed = FALSE), remove.loops = FALSE) 
V(fb_graph)$f_group <- fb_node[, "group"] 

fb_melt <- melt(unique(fb_edge))
fb_melt_w <- dcast(fb_melt, to ~ from)
fb_melt_x <- as.matrix(fb_melt_w[, -1])
fb_melt_x[is.na(fb_melt_x)] <- 0
fb_melt_x <- as.data.frame(apply(fb_melt_x, 2, function(x) as.numeric(x > 0)))
row.names(fb_melt_x) <- fb_melt_w[, 1]
row.names(fb_node) <- fb_node[, 1]
fb_node <- merge(fb_node, fb_melt_x, by = 0, all = TRUE)
row.names(fb_node) <- fb_node[, "Row.names"]
fb_node <- fb_node[, c(4:6)]

fb_fun <- data.frame(V1 = fb_node_ori[c(1:3), 1]) 
fb_fun_x <- as.matrix(dcast(fb_fun, V1 ~ V1))
fb_fun_x[is.na(fb_fun_x)] <- 0
fb_fun_x <- as.data.frame(apply(fb_fun_x, 2, function(x) as.numeric(x > 0)))
row.names(fb_fun_x) <- colnames(fb_fun_x[, c(2:4)]) 
fb_fun_x <- fb_fun_x[, c(2:4)]
fb_node <- rbind(fb_melt_x, fb_fun_x)
fb_node <- fb_node[c(1:98), ] 

# associated diseases of binary network (without statistical result)
gd_edge <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary/Enrichment_QC/GO_DisGeNET_edge.csv", header = T)
gd_node <- read.table("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/metascape/binary/Enrichment_QC/GO_DisGeNET_node.txt", sep = "\t", header = T)
gd_graph <- graph_from_data_frame(gd_edge, directed = FALSE)
V(gd_graph)$d_group <- gd_node[, 2]

# union of viral-host-host-function network
viral_host_func <- union(binary_merge, fb_graph)

# create network in cytoscape
# createNetworkFromIgraph(graph, title = "HuRI", collection = "HuRI") # not very efficiency with RCy3 with big network
createNetworkFromIgraph(binary_merge, title = "viral-host-host network2", collection = "Binary network", )
createNetworkFromIgraph(binary_sub_graph, title = "host-host network", collection = "Y2H networks", )

createNetworkFromIgraph(binary_graph, title = "viral-host network", collection = "Binary network")
# deleteNetwork(network = "Functional Category")
createNetworkFromIgraph(fb_graph, title = "Functional Category", collection = "Functional analysis")
# deleteNetwork(network = "viral-host-host-function")
createNetworkFromIgraph(viral_host_func, title = "viral-host-host-function", collection = "viral-host-host-function")
# createNetworkFromIgraph(gd_graph, title = "Disease Category", collection = "Functional analysis")
loadTableData(fb_node)
# loadTableData(gd_node)
# mergeNetworks(sources = c("viral-host-host network", "Functional Category"), title = "merged_all", operation = "union") # only two at once is do able

# deleteVisualStyle("VirHostome")
nodecolor <- colorRampPalette(brewer.pal(3, "RdYlBu"))
fb_nodecolor <- nodecolor(3) # try custom summary

style.name <- "VirHostome"
defaults <- list(NODE_SHAPE = "ellipse",
                 NODE_SIZE = 30,
                 EDGE_TRANSPARENCY = 120,
                 NODE_LABEL_POSITION = "W, E, c, 0.00, 0.00",
                 NODE_FILL_COLOR = "#00bfff",
                 NODE_Border_Width = 0)
nodeLabels <- mapVisualProperty(visual.prop = "node label",
                table.column = "name",
                mapping.type = "p")
nodeFills <- mapVisualProperty(visual.prop = "node fill color",
             table.column = "group",
             mapping.type = "d",
             table.column.values = "virus",
             visual.prop.values = "#ff0000")
# deleteVisualStyle(style.name)
createVisualStyle(style.name, defaults, list(nodeLabels, nodeFills))

style.name_f <- "VirHostome_f_m"
f_nodeFills <- mapVisualProperty(visual.prop = "node fill color",
             table.column = "name",
             mapping.type = "d",
             table.column.values = names(fb_node),
             visual.prop.values = fb_nodecolor)
# deleteVisualStyle(style.name_f)
createVisualStyle(style.name_f, defaults, list(nodeLabels, f_nodeFills))

setVisualStyle(style.name, "viral-host-host network")
setVisualStyle(style.name_f, "Functional Category")
setVisualStyle(style.name_f, "viral-host-host-function")

setNodeCustomPieChart(names(fb_node), colors = fb_nodecolor, style.name = "VirHostome_f_m", slot = 9)
setNodeBorderOpacityDefault(0, style.name = style.name_f)
```

### show human target associated functional categories into viral protein node
```{r}
binary_function <- binary_graph %u% fb_graph
viral_f <- data.frame(matrix(ncol = 8, nrow = 19))
names(viral_f) <- names(fb_node)
row.names(viral_f) <- sort(unique(binary_edge$virus))
for (i in row.names(viral_f)) {
  viral_f[i, ] <- names(fb_node) %in% sort(unique(names(fb_node)[match(names(unlist(ego(binary_function, order = 2, node = i))), names(fb_node))], na.rm = TRUE))
}
viral_f <- viral_f * 1 # Cool answer from https://stackoverflow.com/questions/33930188/convert-dataframe-column-to-1-or-0-for-true-false-values-and-assign-to-dataf
fb_node <- rbind(fb_node, viral_f)
loadTableData(fb_node)
setNodeCustomPieChart(names(fb_node), colors = fb_nodecolor, style.name = style.name_f, slot = 9)
```

### play the visualization of VirHostome network
```{r}
# addCyNodes(c("viral protein", "human protein")) # don't know how to put legend into the network.
fitContent()
exportImage(filename = '/Users/chung-wen.lin/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/viral-host-host.pdf', type = "PDF", network = "viral-host-host-function")
# the exportImage function is not that good, node labels are ignored

selectNodes(by.col = "group", nodes = "virus")
```

## have level 1 and 2 neighborhood
### for HuRI
```{r message = FALSE}
for (i in 1:length(binary)) {
  neighbor_plot <- make_ego_graph(graph, order = 1, nodes = binary[i], mode = "all")
  V(neighbor_plot[[1]])$group <- ifelse(names(V(neighbor_plot[[1]])) %in% binary, "virus", "")
  createNetworkFromIgraph(simplify(neighbor_plot[[1]], remove.loops = FALSE), title = paste0("L2_from_", binary[i]), collection = "HuRI")
  setVisualStyle(style.name, paste0("L1_from_", binary[i]))
  layoutNetwork("force-directed")

    neighbor_plot <- make_ego_graph(graph, order = 2, nodes = binary[i], mode = "all")
  V(neighbor_plot[[1]])$group <- ifelse(names(V(neighbor_plot[[1]])) %in% binary, "virus", "")
  createNetworkFromIgraph(simplify(neighbor_plot[[1]], remove.loops = FALSE), title = paste0("L2_from_", binary[i]), collection = "HuRI")
  setVisualStyle(style.name, paste0("L2_from_", binary[i]))
  layoutNetwork("force-directed")
}
```

### for HI-union
```{r}
for (i in 78:length(binary)) {
  neighbor_plot <- make_ego_graph(hi_graph, order = 1, nodes = binary[i], mode = "all")
  V(neighbor_plot[[1]])$group <- ifelse(names(V(neighbor_plot[[1]])) %in% binary, "virus", "")
  createNetworkFromIgraph(simplify(neighbor_plot[[1]], remove.loops = FALSE), title = paste0("L1_from_", binary[i]), collection = "Hi-union")
#  setVisualStyle(style.name, paste0("L1_from_", binary[i]))
#  layoutNetwork("force-directed")
    Sys.sleep(5)

    neighbor_plot <- make_ego_graph(hi_graph, order = 2, nodes = binary[i], mode = "all")
  V(neighbor_plot[[1]])$group <- ifelse(names(V(neighbor_plot[[1]])) %in% binary, "virus", "")
  createNetworkFromIgraph(simplify(neighbor_plot[[1]], remove.loops = FALSE), title = paste0("L2_from_", binary[i]), collection = "Hi-union")
#  setVisualStyle(style.name, paste0("L2_from_", binary[i]))
#  layoutNetwork("force-directed")
  Sys.sleep(10)
}

```


## doing community calculation
based on entire HuRI network
```{r}
# Community structure detection based on edge betweenness
## very time consuming
## **18 Nov, 2020**, done on scm server
###################################
# by edge_betweenness, on scm server

# library(igraph)
# huri <- read.csv("HuRI_Tong_withSymbol.csv", header = T)
# huri <- huri[, c(5:6)]
# huri_graph <- graph_from_data_frame(huri, directed = FALSE)
# huri_eb <- cluster_edge_betweenness(huri_graph, directed = FALSE)
# save.image(file = "HuRI_edgebetweenness.RData")
#####
# the above HuRI_edgebetweenness.RData was merged with linkCommunity.RData into HuRI_communities.RData
#####
###################################
load("~/Documents/INET-work/virus_network/statistic_results/HuRI_communities.RData")
ceb_tb <- membership(huri_eb)
ceb_df <- as.data.frame(matrix(ceb_tb))
names(ceb_df) <- "EdgeBetweennessCommunity"
ceb_df$gene <- names(ceb_tb)
ceb_df <- ceb_df[order(ceb_df$community, ceb_df$group), ]
write.table(ceb_df[, c(2, 1, 3)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_eb_df.csv", sep = ",", row.names = FALSE)

# Community strucure via short random walks
cw <- cluster_walktrap(graph)

# Community structure via greedy optimization of modularity
cfg <- cluster_fast_greedy(simplify(graph))

# propagating labels
clp <- cluster_label_prop(graph)

# Community structure detecting based on the leading eigenvector of the community matrix
cle <- cluster_leading_eigen(graph)

# Finding community structure by multi-level optimization of modularity
cl <- cluster_louvain(graph)

# based on Generate Overlapping Cluster Generator (OCG) Communities
lc_ocg <- getOCG.clusters(huri)

# based on edge similarity, only analyze viral-host-host network
# graph_df <- unique(as_data_frame(graph))
# lc <- getLinkCommunities(graph_df, use.all.edges = TRUE, edglim = 10^6)
lc_clusters <- lengths(lc$clusters)
lc_df_edges <- as.data.frame(lc$edges)
lc_df_edges$sharename <- paste0(lc_df_edges$node1, " (interacts with) ", lc_df_edges$node2)
lc_df_edgelist <- as.data.frame(lc$edgelist)
lc_df_edgelist$sharename <- paste0(lc_df_edgelist$V1, " (interacts with) ", lc_df_edgelist$V2)
lc_df_edgelist$cluster <- lc_df_edges[match(lc_df_edgelist$sharename, lc_df_edges$sharename), "cluster"]
names(lc_clusters) <- c(1:length(lc_clusters))

barplot(lc_clusters, xlab = "community", ylab = "size", las = 1, col = barcolor(length(lc_clusters)))
write.table(lc_df_edgelist, file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_linkcomm_edge_community.csv", sep = ",", row.names = FALSE)

par(mfrow = c(2, 3))
barplot(sizes(ceb), main = "ceb", xlab = "community", ylab = "size", las = 1)
barplot(log(sizes(cw), 10), main = "cw", xlab = "community", ylab = "size (log10)", las = 1)
barplot(log(sizes(cfg), 10), main = "cfg", xlab = "community", ylab = "size (log10)", las = 1)
barplot(log(sizes(clp), 10), main = "clp", xlab = "community", ylab = "size (log10)", las = 1)
barplot(log(sizes(cle), 10), main = "cle", xlab = "community", ylab = "size (log10)", las = 1)
barplot(log(sizes(cl), 10), main = "cl", xlab = "community", ylab = "size (log10)", las = 1)

# visualization of individual community from link community
pdf("/tmp/huri_lc.pdf")
for (i in seq(1, 1532, by = 4)) {
  plot(lc, type = "graph", vsize = 5, vlabel = TRUE, clusterids = c(i, i+1, i+2, i+3))
  title(main = paste0(i, " to ", i + 3))
}
dev.off()
```

## output statitics of community based on link community and edge-betweenness
**2020.11.22**
```{r}
lc_table <- sort(table(lc_df_edgelist$cluster))
lc_count <- round(as.matrix(summary(as.vector(table(lc_df_edgelist$cluster)))), 0)
# eb <- read.csv("~/Documents/INET-work/virus_network/statistic_results/HuRI_eb_df.csv", header = T)
eb_table <- sort(table(eb$community))
eb_count <- round(as.matrix(summary(as.vector(table(eb$community)))), 0)

pdf("/tmp/HuRI_community.pdf", width = 5, height = 5)
barplot(lc_table, las = 2, xlab = "community", ylab = "count", main = "Community via LinkComm")
grid.table(lc_count)
text(770, 500, "Statistic of community (n = 1532) count", cex = .7)
barplot(eb_table, las = 2, xlab = "community", ylab = "count", main = "Community via edgeBetweenness")
grid.table(eb_count)
text(220, 700, "Statistic of community (n = 412) count", cex = .7)
dev.off()
```
