---
title: enrichment analysis
author: Lin Chung-wen
date: 2020.12.07
output: html_document
---
## loading enviroment set and data
```{r}
library(gprofiler2)
library(dplyr)
library(rstatix)
library(igraph)
library(stringr)
library(linkcomm)
library(RCy3)

# load("~/Documents/INET-work/virus_network/statistic_results/HuRI_ocg_assays.RData")
load("~/Documents/INET-work/virus_network/statistic_results/HuRI_ocg.RData")
# load("~/Documents/INET-work/virus_network/statistic_results/HI_union_ocg.RData")

bp_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_HuRI_GOBP_EXP.gmt")
mf_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_HuRI_GOMF_EXP.gmt")
cc_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_HuRI_GOCC_EXP.gmt")

# hi_bp_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_HI_GOBP.gmt")
# hi_mf_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_HI_GOMF.gmt")
# hi_cc_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_HI_GOCC.gmt")
#
# a1_bp_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a1_GOBP.gmt")
# a1_mf_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a1_GOMF.gmt")
# a1_cc_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a1_GOCC.gmt")
#
# a2_bp_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a2_GOBP.gmt")
# a2_mf_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a2_GOMF.gmt")
# a2_cc_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a2_GOCC.gmt")
#
# a3_bp_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a3_GOBP.gmt")
# a3_mf_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a3_GOMF.gmt")
# a3_cc_cust <- upload_GMT_file(gmtfile = "~/workplace/database/hsapien_a3_GOCC.gmt")
#
# hpo <- upload_GMT_file(gmtfile = "~/workplace/database/human_phenotype_pho.gmt")
# binary_ori <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/binary_node_1126.csv", header = T)
#
# hpa <- upload_GMT_file(gmtfile = "~/workplace/database/HPA/normal_tissue_only.gmt")

# hpa_protein <- upload_GMT_file(gmtfile = "~/workplace/database/HPA/HPA_protein.gmt") # error 400

# hpa_bp <- upload_GMT_file(gmtfile = "~/workplace/database/HPA/HPA_bp.gmt")

funcEnrich <- function(ocg, organism, querylist) {
    go <- list()
    df <- data.frame("name" = names(ocg$clustsizes), "clustsize" = ocg$clustsizes)
    for (i in querylist) {
        query_list <- ocg[[4]][ocg[[4]][, 2] == i, "node"]
        goquery <- gost(query = query_list, organism = organism, correction_method = "bonferroni", evcodes = TRUE)
        goquery$result$inCommunity <- paste0( goquery$meta$query_metadata$queries$query_1, collapse = ",")
        goquery$result$annotatedInCommunity <- paste0(goquery$meta$genes_metadata$query$query_1$ensgs, collapse = ",")
        target <- query_list[query_list %in% binary$node]
        goquery$result$viralTarget <- paste0(target, collapse = ",")
        go[[i]] <- goquery$result
    }
    return(go)
}

statCal <- function(ocg, virTarget, totalN) {
        clust <- ocg$nodeclusters
        clust2 <- clust %>% select(cluster) %>% group_by(cluster) %>% mutate(count = n()) %>% distinct()
        df <- ocg$nodeclusters[ocg$nodeclusters$node %in% binary_node, ]
        df2 <- df %>% select(cluster) %>% group_by(cluster) %>% mutate(count = n()) %>% distinct()
        merged <- merge(clust2, df2, by = "cluster", all.x = TRUE)
        merged[is.na(merged)] <- 0
        merged$notTarget <- merged[, 2] - merged[, 3]
        # merged$cluster <- merged$cluster
        row.names(merged) <- merged[, 1]
        merged <- merged[, c(3, 4)]
        names(merged) <- c("Target", "notTarget")
        total <- c(virTarget, totalN - virTarget)
        names(total) <- c("Target", "notTarget")
        data <- data.frame()
        data <- apply(merged, 1, function(x) {
                tab <- rbind(x, total)
                fisher_test(tab)
                })
        return(data)
}

goOutput <- function(ocg, ocgbp) {
        ocg1 <- statCal(ocg, length(binary_node), length(unique(ocg$nodeclusters$node)))
        ocg1_all <- do.call(rbind.data.frame, ocg1)
        ocg1_all$cluster <- row.names(ocg1_all)
        ocg1_graph <- ocg1_all[ocg1_all$p <= 0.05, "cluster"]

        dfa1 <- list()
        for (i in ocg1_graph$cluster) {
                if (length(ocgbp[[i]]) != 19) {
                        next
                } else {
                        dfa1[i] <- ocgbp[i]
                }
        }
        ocga1_bp <- do.call(rbind, dfa1)
}

toCyto <- function(selected, assayOCG, assayC, networkName) {
        for (i in selected) {
                setCurrentNetwork(network = assayC)
                clearSelection()
                sel <- getNodesIn(assayOCG, clusterids = i)
                selectNodes(sel, by.col = "name", network = assayC)
                createSubnetwork(subnetwork.name = paste0(networkName, "_community_", i))
                setVisualStyle(style.name, paste0(networkName, "_community_", i))
                layoutNetwork("force-directed")
        }
}

# export significant GO terms
export <- function(go, checklist) {
    dfa1 <- list()
    for (i in checklist) {
        if(length(go[[i]]) == 19) {
            dfa1[i] <- go[i]
            dfa1[[i]]$cluster <- i
        } else {
            next
        }
    }
    return(dfa1)
}
```

## summary for HuRI community
```{r}
clust <- huri_ocg$nodeclusters
clust2 <- clust %>% select(cluster) %>% group_by(cluster) %>% mutate(count = n()) %>% distinct() # have community size
df <- huri_ocg$nodeclusters[huri_ocg$nodeclusters$node %in% binary_node, ] # viral target in community
df2 <- df %>% select(cluster) %>% group_by(cluster) %>% mutate(count = n()) %>% distinct() # community viral target size
merged <- merge(clust2, df2, by = "cluster", all.x = TRUE) # merge community size and virtal target
merged[is.na(merged)] <- 0
merged$notTarget <- merged[, 2] - merged[, 3]
row.names(merged) <- merged[, 1]
merged_checkP <- merged[, c(3, 4)]
names(merged_checkP) <- c("Target", "notTarget")

total <- c(171, 8274)
data <- data.frame()
data <- apply(merged_checkP, 1, function(x) {
    tab <- rbind(x, total)
    fisher_test(tab)
    })

pvalue <- c()
for (i in 1:length(data)) {
    pvalue <- c(pvalue, data[[i]]$p)
}
padj <- p.adjust(pvalue, method = "fdr")

huri_ocg_enrich <- do.call(rbind.data.frame, data)
huri_ocg_enrich$cluster <- row.names(huri_ocg_enrich)
huri_all <- cbind(merged, huri_ocg_enrich, padj)
names(huri_all) <- c("community", "community_size", "viral_target", "notTarget", "n", "p", "p.signif", "community_2", "p_adjust (fdr)")
write.csv(huri_all[, c(1, 2, 3, 6, 7, 9)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_signif_community.csv", row.names = F)

check_list <- huri_all[huri_all[, 2] > 3 & huri_all[, 6] < 0.05, 1] # based on community size and fisher test p value

pdf("~/Documents/INET-work/virus_network/figure_results/HuRI_community_distribution.pdf", width = 7, height = 5)
layout(matrix(c(1, 1, 2), nrow = 1, byrow = TRUE))
barplot(table(huri_ocg$clustsizes), las = 1, xlab = "size", ylab = "count")
text(16, 600, labels = "Size:\n
    Min: 1\n
    1st Qu: 4\n
    Median: 5\n
    3rd Qu: 6\n
    Max: 16", pos = 2)
boxplot(huri_ocg$clustsizes, las = 1, ylab = "size")
dev.off()
```

## running GO functional enrichment analysis
```{r}
binary <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/binary_node_1126_simple.csv", header = T)
binary_node <- unique(binary[binary$category == "human", "node"])

# subDir <- "ocg1"
# dir.create(file.path(subDir), showWarnings = FALSE)
# setwd(file.path(subDir))

huri_ocg_gobp <- funcEnrich(huri_ocg, bp_cust, check_list)
huri_ocg_gomf <- funcEnrich(huri_ocg, mf_cust, check_list)
huri_ocg_gocc <- funcEnrich(huri_ocg, cc_cust, check_list)

# huri_ocg1_gobp <- funcEnrich(huri_ocg1, a1_bp_cust, 5)
# huri_ocg1_gomf <- funcEnrich(huri_ocg1, a1_mf_cust, 5)
# huri_ocg1_gocc <- funcEnrich(huri_ocg1, a1_cc_cust, 5)
#
# huri_ocg2_gobp <- funcEnrich(huri_ocg2, a2_bp_cust, 5)
# huri_ocg2_gomf <- funcEnrich(huri_ocg2, a2_mf_cust, 5)
# huri_ocg2_gocc <- funcEnrich(huri_ocg2, a2_cc_cust, 5)
#
# huri_ocg3_gobp <- funcEnrich(huri_ocg3, a3_bp_cust, 5)
# huri_ocg3_gomf <- funcEnrich(huri_ocg3, a3_mf_cust, 5)
# huri_ocg3_gocc <- funcEnrich(huri_ocg3, a3_cc_cust, 5)
#
# hi_ocg_gobp <- funcEnrich(hi_ocg, hi_bp_cust, 5)
# hi_ocg_gomf <- funcEnrich(hi_ocg, hi_mf_cust, 5)
# hi_ocg_gocc <- funcEnrich(hi_ocg, hi_cc_cust, 5)

# not doable here
# library(EnrichmentBrowser)
# getGenesets(org = "hsa", db = "go", onto = "BP", mode = "GO.db", gs = huri_ocg1[[4]][huri_ocg1[[4]][, 2] == i, "node"])
# pwys <- downloadPathways("hsa")
# not doable here

# using GOA dataset
# url: http://current.geneontology.org/products/pages/downloads.html
# http://geneontology.org/gene-associations/goa_human.gaf.gz
```

## Community and viral-host integration
load interaction pair information and have network visualization in Cytoscape
```{r}
huri <- read.table("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_edges.txt", header = F, sep = "\t")
huri_node <- unique(c(huri$V1, huri$V2))
binary <- read.csv("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/binary_node_1126_simple.csv", header = T)
binary_node <- unique(binary[binary$category == "human", "node"])
df <- data.frame("name" = huri_node, "viralTarget" = ifelse(huri_node %in% binary[binary$category == "human", "node"], "yes", "no"))

huri_graph <- graph_from_data_frame(huri, directed = FALSE)
createNetworkFromIgraph(huri_graph, title = "HuRI", collection = "HuRI", )
row.names(df) <- df$name
loadTableData(df)
createColumnFilter(filter.name = "viral", column = "viralTarget", "yes", predicate = "IS", network = "HuRI")
createSubnetwork(subnetwork.name = "viralTargets")

huri_a1 <- read.table("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_assay1_edges.txt", header = F, sep = "\t")
huri_a2 <- read.table("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_assay2_edges.txt", header = F, sep = "\t")
huri_a3 <- read.table("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_assay3_edges.txt", header = F, sep = "\t")
huri_a1_graph <- graph_from_data_frame(huri_a1, directed = FALSE)
createNetworkFromIgraph(huri_a1_graph, title = "HuRI_a1", collection = "HuRI", )
huri_a2_graph <- graph_from_data_frame(huri_a2, directed = FALSE)
createNetworkFromIgraph(huri_a2_graph, title = "HuRI_a2", collection = "HuRI", )
huri_a3_graph <- graph_from_data_frame(huri_a3, directed = FALSE)
createNetworkFromIgraph(huri_a3_graph, title = "HuRI_a3", collection = "HuRI", )
```

### HuRI
```{r}
gobp <- export(huri_ocg_gobp, check_list)
gobp_df <- do.call(rbind.data.frame, gobp)
gomf <- export(huri_ocg_gomf, check_list)
gomf_df <- do.call(rbind.data.frame, gomf)
gocc <- export(huri_ocg_gocc, check_list)
gocc_df <- do.call(rbind.data.frame, gocc)

go_final <- rbind(gobp_df[, c(20, 2:13, 15:19)], gomf_df[, c(20, 2:13, 15:19)], gocc_df[, c(20, 2:13, 15:19)])

write.csv(go_final, file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_signif_community_GO.csv", row.names = FALSE)

toPlot <- unique(c(str_extract(row.names(ocgRI_bp), pattern = "^[0-9]+"),
                str_extract(row.names(ocgRI_mf), pattern = "^[0-9]+"),
                str_extract(row.names(ocgRI_cc), pattern = "^[0-9]+")))
#toCyto(toPlot, huri_ocg, "HuRI", "HuRI")
```

### HuRI assay1
```{r}
huri_ocg1_enrich <- do.call(rbind.data.frame, statCal(huri_ocg1, length(binary_node), length(unique(huri_ocg1$nodeclusters$node))))
huri_ocg1_enrich$cluster <- row.names(huri_ocg1_enrich)
write.table(huri_ocg1_enrich[huri_ocg1_enrich$"p.signif" < 0.05, ], file = "~/Documents/INET-work/virus_network/statistic_results/HuRIassay1_signif_community.csv", sep = ",")

ocga1_bp <- goOutput(huri_ocg1, huri_ocg1_gobp)
ocga1_mf <- goOutput(huri_ocg1, huri_ocg1_gomf)
ocga1_cc <- goOutput(huri_ocg1, huri_ocg1_gocc)
toPlot <- unique(c(str_extract(row.names(ocga1_bp), pattern = "^[0-9]+"),
                str_extract(row.names(ocga1_mf), pattern = "^[0-9]+"),
                str_extract(row.names(ocga1_cc), pattern = "^[0-9]+")))
# toCyto(toPlot, huri_ocg1, "HuRI_a1", "assay1")
write.table(rbind(ocga1_bp, ocga1_mf, ocga1_cc)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_a1_GO.csv", sep = ",")
```

### HuRI assay2
```{r}
huri_ocg2_enrich <- do.call(rbind.data.frame, statCal(huri_ocg2, length(binary_node), length(unique(huri_ocg2$nodeclusters$node))))
huri_ocg2_enrich$cluster <- row.names(huri_ocg2_enrich)
write.table(huri_ocg2_enrich[huri_ocg2_enrich$"p.signif" < 0.05, ], file = "~/Documents/INET-work/virus_network/statistic_results/HuRIassay2_signif_community.csv", sep = ",")

ocga2_bp <- goOutput(huri_ocg2, huri_ocg2_gobp)
ocga2_mf <- goOutput(huri_ocg2, huri_ocg2_gomf)
ocga2_cc <- goOutput(huri_ocg2, huri_ocg2_gocc)
toPlot <- unique(c(str_extract(row.names(ocga2_bp), pattern = "^[0-9]+"),
                str_extract(row.names(ocga2_mf), pattern = "^[0-9]+"),
                str_extract(row.names(ocga2_cc), pattern = "^[0-9]+")))
# toCyto(toPlot, huri_ocg2, "HuRI_a2", "assay2")
write.table(rbind(ocga2_bp, ocga2_mf, ocga2_cc)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_a2_GO.csv", sep = ",")
```

### HuRI assay3
```{r}
huri_ocg3_enrich <- do.call(rbind.data.frame, statCal(huri_ocg3, length(binary_node), length(unique(huri_ocg3$nodeclusters$node))))
huri_ocg3_enrich$cluster <- row.names(huri_ocg3_enrich)
write.table(huri_ocg3_enrich[huri_ocg3_enrich$"p.signif" < 0.05, ], file = "~/Documents/INET-work/virus_network/statistic_results/HuRIassay3_signif_community.csv", sep = ",")

ocga3_bp <- goOutput(huri_ocg3, huri_ocg3_gobp)
ocga3_mf <- goOutput(huri_ocg3, huri_ocg3_gomf)
ocga3_cc <- goOutput(huri_ocg3, huri_ocg3_gocc)
toPlot <- unique(c(str_extract(row.names(ocga3_bp), pattern = "^[0-9]+"),
                str_extract(row.names(ocga3_mf), pattern = "^[0-9]+"),
                str_extract(row.names(ocga3_cc), pattern = "^[0-9]+")))
# toCyto(toPlot, huri_ocg3, "HuRI_a3", "assay3")
write.table(rbind(ocga3_bp, ocga3_mf, ocga3_cc)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_a3_GO.csv", sep = ",")
```

### HI-union
**Different background for functional enrichment analysis**
```{r}
hi_ocg_enrich <- do.call(rbind.data.frame, statCal(hi_ocg, length(binary_node), length(unique(hi_ocg$nodeclusters$node))))
hi_ocg_enrich$cluster <- row.names(hi_ocg_enrich)
write.table(hi_ocg_enrich[hi_ocg_enrich$"p.signif" < 0.05, ], file = "~/Documents/INET-work/virus_network/statistic_results/HI_signif_community.csv", sep = ",")

ocgHI_bp <- goOutput(hi_ocg, hi_ocg_gobp)
ocgHI_mf <- goOutput(hi_ocg, hi_ocg_gomf)
ocgHI_cc <- goOutput(hi_ocg, hi_ocg_gocc)
toPlot <- unique(c(str_extract(row.names(ocgHI_bp), pattern = "^[0-9]+"),
                str_extract(row.names(ocgHI_mf), pattern = "^[0-9]+"),
                str_extract(row.names(ocgHI_cc), pattern = "^[0-9]+")))
# toCyto(toPlot, hi_ocg, "HI-union", "HI")
write.table(rbind(ocgHI_bp, ocgHI_mf, ocgHI_cc)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_HI_GO.csv", sep = ",")
```

## running HPO functional enrichment analysis
whole binary interactome and individual community
```{r}
binary_hpo <- gost(binary_ori$node, organism = hpo, correction_method = "bonferroni", evcodes = TRUE) # no significant
huri_hpo_ocg <- funcEnrich(huri_ocg, hpo, 5)
# huri_hpo_ocg1 <- funcEnrich(huri_ocg1, hpo, 5)
# huri_hpo_ocg2 <- funcEnrich(huri_ocg3, hpo, 5)
# huri_hpo_ocg3 <- funcEnrich(huri_ocg2, hpo, 5)
hi_hpo_ocg <- funcEnrich(hi_ocg, hpo, 5)

ocg_huri_hpo <- goOutput(huri_ocg, huri_hpo_ocg)
# ocg1_hpo <- goOutput(huri_ocg1, huri_hpo_ocg1)
# ocg2_hpo <- goOutput(huri_ocg2, huri_hpo_oc2)
# ocg3_hpo <- goOutput(huri_ocg2, huri_hpo_oc3)
ocg_hi_hpo <- goOutput(hi_ocg, hi_hpo_ocg)

write.table(rbind(ocg_huri_hpo)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_hpo.csv", sep = ",")
write.table(rbind(ocg_hi_hpo)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HI_hpo.csv", sep = ",")
```

## running HPA normal tissue enrichment analysis
whole binary interactome and individual community
```{r}
binary_hpa <- gost(binary_ori$node, organism = hpa, correction_method = "bonferroni", evcodes = TRUE) # no significant
huri_hpa_ocg <- funcEnrich(huri_ocg, hpa, 5)
hi_hpa_ocg <- funcEnrich(hi_ocg, hpa, 5)

ocg_huri_hpa <- goOutput(huri_ocg, huri_hpa_ocg)
ocg_hi_hpa <- goOutput(hi_ocg, hi_hpa_ocg)

write.table(rbind(ocg_huri_hpa)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HuRI_hpa.csv", sep = ",")
write.table(rbind(ocg_hi_hpa)[, c(1:13, 15:19)], file = "~/Documents/INET-work/virus_network/statistic_results/HI_hpa.csv", sep = ",")
```
