---
title: Display gene tissue specificity profiles, HuSCI + APMS
date: 2021.03.09
output: html_document
---

# Definition:
> ref: http://bioconductor.statistik.tu-dortmund.de/packages/3.7/bioc/vignettes/TissueEnrich/inst/doc/TissueEnrich.html
> ref: https://www.proteinatlas.org/about/assays+annotation#classification_rna

1. **Tissue-enriched**
    genes with an expression level greater than 1 that also have at least 4-fold higher expression levels in a particular tissue compared to all other tissues.
2. **Group-enriched**
    genes with an expression level greater than 1 that also have at least 4-fold higher expression levels in a group of 2-5 tissues compared to all other tissues, and that are not considered tissue-enriched
3. **Tissue-enhanced**
    genes with an expression level greater than 1 that also have at least 4-fold higher expression levels in a particular tissue compared to the average levels in all other tissues, and that are not considered tissue-enriched or group-enriched.
4. **Low-specificity**
    genes with an expression level greater than or equal to 1 in at least one tissue but not elevated in all any tissues.

# environment setup
```{r message = FALSE}
library(openxlsx)
library(reshape2)
library(ggplot2)
library(ComplexHeatmap)
library(RColorBrewer)
library(circlize)
library(dplyr)
library(pastecs) # https://stats.idre.ucla.edu/r/faq/how-can-i-get-a-table-of-basic-descriptive-statistics-for-my-variables/
library(ggsignif)
# https://stackoverflow.com/questions/52214071/how-to-order-data-by-value-within-ggplot-facets
library(purrr)
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

# 1. loading HPA, HuSCI, Gordon, Li, Stukalov, Nabeel and HuRI data
```{r eval = FALSE}
source("~/Documents/INET-work/virus_network/src/cov_4apms.r", local = knitr::knit_global())
huri <- read.csv("~/Documents/INET-work/references/HuRI_binaryPPI/HuRI_Tong_withSymbol.csv", header = T)
huri_uniq <- unique(c(huri$ensembl_gene_id_a, huri$ensembl_gene_id_b))
# write.xlsx(has_tissue[has_tissue$ensemblID %in% huri_uniq, ], file = "~/Documents/INET-work/virus_network/toSummarize/tissue_specificity/data/HuRI_tissue_HPA.xlsx")
```

```{r}
## VirHostome
category <- c("Group enriched", "Low tissue specificity", "Not detected", "Tissue enhanced", "Tissue enriched")
length <- c(7, 25, 0, 15, 7)
for (i in c(1, 2, 4, 5)) {
    pdf(paste0("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/HuSCI_tissue_", i, ".pdf"), width = 12, height = length[i] * 0.9)
    ht <- Heatmap(as.matrix(husci_rna[husci_rna$RNA_tissue_specificity == category[i], c(6:65)]),
        name = "NX",
        colorRamp2(c(0, max(husci_rna[husci_rna$RNA_tissue_specificity == category[i], c(6:65)], na.rm = T)), c("white", "red")),
        na_col = "gray",
        cluster_columns = FALSE,
        column_split = has_organ,
        column_names_gp = gpar(col = rep(c("red", "blue"), 8)),
        column_title = paste0("SARS2 target proteins tissue preferentially expression - ", category[i]),
        width = unit(8, "inch"), height = unit(length[i] * 0.95, "cm"),
        row_names_gp = gpar(fontsize = 8))
    draw(ht)
    dev.off()
}

write.csv(husci_rna, file = "~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/HuSCI_tissue_exp.csv", row.names = F)
```

### incorporate BioPlex3.0
```{r}
# bioplex3 <- read.delim("~/Documents/INET-work/references/HumanInteractome_APMS/BioPlex.3.0_edge.tsv", sep = "\t", header = T)
bioplex3_id <- read.csv("~/Documents/INET-work/references/HumanInteractome_APMS/IDmap_uniprot_ensembl.csv", header = T)
bioplex3_tissue <- has_tissue[has_tissue$ensemblID %in% bioplex3_id$Ensembl, ]

```

# 2. display ratio of tissue specific genes in human genome and SARS-CoV-2 interactome
**2021.03.23 22:22**- manual calculate tissue specificity

```{r eval = FALSE}
write.csv(gordon_rna, file = "~/Documents/INET-work/virus_network/statistic_results/gordon_tissue_rna.csv", row.names = F)
write.csv(stukalov_rna, file = "~/Documents/INET-work/virus_network/statistic_results/stukalov_tissue_rna.csv", row.names = F)
write.csv(li_rna, file = "~/Documents/INET-work/virus_network/statistic_results/li_tissue_rna.csv", row.names = F)
write.csv(nabeel_rna, file = "~/Documents/INET-work/virus_network/statistic_results/nabeel_tissue_rna.csv", row.names = F)
write.csv(bioid_rna, file = "~/Documents/INET-work/virus_network/statistic_results/bioid_laurent_tissue_rna.csv", row.names = F)
write.csv(bioid_st_rna, file = "~/Documents/INET-work/virus_network/statistic_results/bioid_ST_tissue_rna.csv", row.names = F)
write.csv(bioid_sama_rna, file = "~/Documents/INET-work/virus_network/statistic_results/bioid_SAMA_tissue_rna.csv", row.names = F)
```

### count ratio of gene-tissue specificity
```{r message = FALSE}
table_all_s <- prop.table(table(has_all$RNA.tissue.specificity))
table_all_d <- prop.table(table(has_all$RNA.tissue.distribution))

table_husci_s <- prop.table(table(husci_rna$RNA_tissue_specificity))
table_husci_d <- prop.table(table(husci_rna$RNA_tissue_distribution))

table_gordon_s <- prop.table(table(gordon_rna$RNA_tissue_specificity))
table_gordon_s["Not detected"] <- 0
table_gordon_d <- prop.table(table(gordon_rna$RNA_tissue_distribution))
table_gordon_d["Detected in single"] <- 0
table_gordon_d["Not detected"] <- 0

table_stukalov_s <- prop.table(table(stukalov_rna$RNA_tissue_specificity))
table_stukalov_s["Not detected"] <- 0
table_stukalov_d <- prop.table(table(stukalov_rna$RNA_tissue_distribution))
table_stukalov_d["Not detected"] <- 0

table_li_s <- prop.table(table(li_rna$RNA_tissue_specificity))
table_li_s["Not detected"] <- 0
table_li_d <- prop.table(table(li_rna$RNA_tissue_distribution))
table_li_d["Not detected"] <- 0

table_nabeel_s <- prop.table(table(nabeel_rna$RNA_tissue_specificity))
table_nabeel_s["Not detected"] <- 0
table_nabeel_d <- prop.table(table(nabeel_rna$RNA_tissue_distribution))
table_nabeel_d["Detected in single"] <- 0
table_nabeel_d["Not detected"] <- 0
# BioID Laurent
table_bioid_s <- prop.table(table(bioid_rna$RNA_tissue_specificity))
table_bioid_s["Not detected"] <- 0
table_bioid_d <- prop.table(table(bioid_rna$RNA_tissue_distribution))
table_bioid_d["Not detected"] <- 0
# BioID St-Germain
table_bioidST_s <- prop.table(table(bioid_st_rna$RNA_tissue_specificity))
table_bioidST_s["Not detected"] <- 0
table_bioidST_d <- prop.table(table(bioid_st_rna$RNA_tissue_distribution))
table_bioidST_d["Not detected"] <- 0
# BioID Samavarchi
table_bioidSA_s <- prop.table(table(bioid_sama_rna$RNA_tissue_specificity))
table_bioidSA_s["Not detected"] <- 0
table_bioidSA_d <- prop.table(table(bioid_sama_rna$RNA_tissue_distribution))
table_bioidSA_d["Not detected"] <- 0

table_d_order <- c(1, 2, 4, 3, 5)
table_specificity <- rbind(HPA = table_all_s, HuSCI = table_husci_s, Gordon = table_gordon_s[c(1, 2, 5, 3, 4)], Stukalov = table_stukalov_s[c(1, 2, 5, 3, 4)], Li = table_li_s[c(1, 2, 5, 3, 4)], Nabeel = table_nabeel_s[c(1, 2, 5, 3, 4)], Laurent = table_bioid_s[c(1, 2, 5, 3, 4)], St_Germain = table_bioidST_s[c(1, 2, 5, 3, 4)], Samavarchi = table_bioidSA_s[c(1, 2, 5, 3, 4)])
table_distribution <- rbind(HPA = table_all_d[table_d_order], HuSCI = table_husci_d[table_d_order], Gordon = table_gordon_d, Stukalov = table_stukalov_d[table_d_order], Li = table_li_d[table_d_order], Nabeel = table_nabeel_d, Laurent = table_bioid_d[table_d_order], St_Germain = table_bioidST_d[table_d_order], Samavarchi = table_bioidSA_d[table_d_order])

colour <- c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#FF7F00", "#FFFF00", "brown", "grey")
pdf("~/documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/tissue_specificity_withBioID_all.pdf", width = 10, height = 5)
par(mar = c(10, 6, 4, 2), mfrow = c(1, 2))
barplot(table_specificity[c(2:9, 1), c(2, 5, 4, 1)] * 100, beside = T, las = 2,
    ylab = "% of genes",
    main = "Specificity",
    ylim = c(0, 100), col = colour)
legend("topright", legend = c("HuSCI", "Gordon", "Stukalov", "Li", "Nabeel", "Laurent", "St_Germain", "Samavarchi", "HPA"),
    fill = colour, ncol = 1, cex = .75, bty = "n")
barplot(table_distribution[c(2:9, 1), c(1:4)] * 100, beside = T, las = 2,
    ylab = "% of genes",
    main = "Distribution",
    ylim = c(0, 100), col = colour)
legend("topright", legend = c("HuSCI", "Gordon", "Stukalov", "Li", "Nabeel", "Laurent", "St_Germain", "Samavarchi", "HPA"),
    fill = colour, ncol = 1, cex = .75, bty = "n")
dev.off()
```

# 3. have SARS-CoV-2 infected tissue profiles
```{r}
dorward <- read.xlsx("~/Documents/INET-work/virus_network/references/tissue_specific/Dorward_immunopathology/figE4_number.xlsx", sheet = 2)
rownames(dorward) <- dorward$tissue
small_mat <- as.matrix(dorward[, c(3:13)]) * 100
pdf("~/Documents/INET-work/virus_network/references/tissue_specific/Dorward_immunopathology/figE4.pdf", height = 4, width = 8)
ht_dorward <- Heatmap(small_mat, colorRamp2(c(0, 100), c("white", "red")), name = "%", cell_fun = function(j, i, x, y, width, height, fill) {
        if(small_mat[i, j] > 0) {
            grid.text(sprintf("%.0f", small_mat[i, j]), x, y, gp = gpar(fontsize = 8))
        } else {
            grid.text("", , x, y, gp = gpar(fontsize = 8))
            }
        },
        column_title = "Tissue specificity of SARS-CoV-2 ORFs in COVID-19 patients")
draw(ht_dorward)
dev.off()
```

# 4. focusing on COVID19 infected tissue
```{r}
infected <- c(9,10,11,12,13,14, 27,28,29,30, 38,39,40,41,42, 43,44, 46,47, 53, 54,55, 56)
infected_list <- list("1" = 9:14, "2" = 27:30, "3" = 38:42, "4" = 43:44, "5" = 46, "6" = 47, "7" = 53, "8" = 54:55, "9" = 56)
for (i in c(1, 2, 4, 5)) {
    pdf(paste0("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/HuSCI_selected_tissue_", i, ".pdf"), width = 7, height = length[i] * 0.9)
    ht <- Heatmap(as.matrix(husci_rna[husci_rna$RNA_tissue_specificity == category[i], c(6:65)])[, infected],
        name = "NX",
        colorRamp2(c(0, max(husci_rna[husci_rna$RNA_tissue_specificity == category[i], c(6:65)][, infected], na.rm = T)), c("white", "red")),
        na_col = "gray",
        column_title = paste0("SARS2 target proteins tissue preferentially expression - ", category[i]),
        width = unit(3.5, "inch"), height = unit(length[i] * 0.95, "cm"),
        row_names_gp = gpar(fontsize = 8))
    draw(ht)
    dev.off()
}
```

# 5. display proportion of host targets in viral proteins and tissue
### NOT useful
```{r eval = FALSE}
husci_g <- read.csv("~/workplace/HuSCI_tissue_exp.csv", header = T)
for (i in unique(husci_g$viral_target)) {
    print(i)
    print(table(husci_g[husci_g$viral_target == i, "RNA_tissue_specificity"]))
}
```

# 6. proportion of host targets in "tissue" level of HuSCI and Gordon data
**2021.03.23 Not that useful**-

```{r message = FALSE, eval = FALSE}
output_tissue <- function(df_in) {
    tissue_prop <- list()
    for (j in 1:9) {
        df <- df_in %>% select(6:65) %>% select(infected_list[[j]])
        tissue_prop[[j]] <- stat.desc(t(df))[8, ]
    }
    tissue_df <- t(do.call(rbind, lapply(tissue_prop, as.data.frame)))
    colnames(tissue_df) <- c("lymphoid", "endocreine", "gastrointestinal", "kidney", "liver", "lung", "heart", "muscle", "pancreases")
    tissue_df <- cbind(tissue_df, df_in$Gene)
    return(tissue_df)
}

NX <- 10

query_rna <- list("husci" = husci_rna, "gordon" = gordon_rna, "stukalov" = stukalov_rna, "li" = li_rna, "nabeel" = nabeel_rna, "human" = has_tissue)

tissue_sum <- list()
tissue_spec_count <- list()
for (i in 1:6) {
    tissue_df <- output_tissue(query_rna[[i]])
    tissue_df1 <- tissue_df[, c(1:9)] # remove gene name again

    ## output statistics
    # write.csv(tissue_df, paste0("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/", names(query_rna[i]), ".csv"))
    tissue_df1[is.na(tissue_df1)] <- 0
    tissue_df1_stat <- apply(tissue_df1, 2, function(x) table(x > NX)/length(x)*100) # proportion of NX > 10
    pdf(paste0("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/NX", NX, "_", names(query_rna[i]), ".pdf"))
    par(mar = c(9, 5, 2, 2))
    barplot(tissue_df1_stat, las = 2, ylab = "%")
    title(names(query_rna[i]))
    dev.off()
    tissue_sum[names(query_rna[i])] <- as.data.frame(tissue_df1_stat[2, ])

    ## calculate individual specificity category in tissue specificity subset
    tissue_df_count <- c()
    for (j in c(1, 2, 4, 5)) {
        t1 <- dim(tissue_df[tissue_df[, 10] %in% query_rna[[i]][query_rna[[i]]$RNA_tissue_specificity == category[j], "Gene"], ])[1]
        tissue_df_count <- c(tissue_df_count, t1)
    }

    ## calculate specificity group
    tissue_spec_count[[i]] <- tissue_df_count
}
output <- do.call(cbind, lapply(tissue_sum, as.data.frame))
names(output) <- names(query_rna)
rownames(output) <- colnames(tissue_df1)
output$tissue <- rownames(output)
mt <- melt(output)
pdf(paste0("~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/tissue_specifici_NX", NX, "_summary.pdf"))
ggplot(mt, aes(x = tissue, y = value, fill = variable)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_brewer(palette = "Spectral") +
    labs(x = "Selected tissues and organs", y = "%", fill = "Interactome data", title = paste0("# of NX > ", NX)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, color = "black", size = 12))
dev.off()
```

# 7. "tissue" level for specific data
```{r message = FALSE}
meltToMatrix <- function(input) {
    m_melt <- melt(unique(input))
    m_melt_w <- dcast(m_melt, from ~ to)
    m_melt_x <- as.matrix(m_melt_w[, -c(1:2)])
    m_melt_x[is.na(m_melt_x)] <- 0
    m_melt_x <- as.data.frame(apply(m_melt_x, 2, function(x) as.numeric(x > 0)))
    row.names(m_melt_x) <- m_melt_w[, 1]
    m_melt_x$ensemblID <- m_melt_w[, 1]
    return(m_melt_x)
}
colSum <- function(input, start, end) {
    df <- input[, c(start:end)]
    return(colSums(df))
    }

husci_r_melt <- meltToMatrix(husci_r)
husci_r_merge <- merge(husci_rna, husci_r_melt, by.x = "ensemblID", by.y = "ensemblID")

gordon_r_melt <- meltToMatrix(gordon_r)
gordon_r_merge <- merge(gordon_rna, gordon_r_melt, by.x = "ensemblID", by.y = "ensemblID")

li_r_melt <- meltToMatrix(li_r)
li_r_merge <- merge(li_rna, li_r_melt, by.x = "ensemblID", by.y = "ensemblID")

stukalov_r_melt <- meltToMatrix(stukalov_r)
stukalov_r_merge <- merge(stukalov_rna, stukalov_r_melt, by.x = "ensemblID", by.y = "ensemblID")

nabeel_r_melt <- meltToMatrix(nabeel_r)
nabeel_r_merge <- merge(nabeel_rna, nabeel_r_melt, by.x = "ensemblID", by.y = "ensemblID")

bioid_r_melt <- meltToMatrix((bioid_r))
```

```{r eval = FALSE}
write.csv(husci_r_merge, file = "~/Documents/INET-work/virus_network/statistic_results/husci_tissue_specificity.csv")
write.csv(gordon_r_merge, file = "~/Documents/INET-work/virus_network/statistic_results/gordon_tissue_specificity.csv")
write.csv(li_r_merge, file = "~/Documents/INET-work/virus_network/statistic_results/li_tissue_specificity.csv")
write.csv(stukalov_r_merge, file = "~/Documents/INET-work/virus_network/statistic_results/stukalov_tissue_specificity.csv")
write.csv(nabeel_r_merge, file = "~/Documents/INET-work/virus_network/statistic_results/nabeel_tissue_specificity.csv")
```
# 8. manual calculate above csv files, then generate plot
```{r message = FALSE}
# in %
sum5 <- read.xlsx("~/Documents/INET-work/virus_network/statistic_results/5interactome_specificity_percentage.xlsx", sheet = 2)
sum5_melt <- melt(sum5)
sum5_melt$data <- factor(sum5_melt$data, levels = c("HuSCI", "Gordon", "Li", "Stukalov", "Nabeel"))

gp <- ggplot(sum5_melt, aes(x = data, y = value * 100)) +
    geom_bar(aes(fill = data), position = "dodge", stat = "identity") +
    # geom_signif(comparisons = list(c("HuSCI", "Gordon"), c("HuSCI", "Li"), c("HuSCI", "Stukalov"), c("HuSCI", "Nabeel")),
    #     test = "t.test",
    #     map_signif_level = TRUE,
    #     y_position = c(7, 8, 9, 10)) +
    ylim(0, 12) +
    labs(x = "", y = "% of host protein") +
    facet_wrap(~ variable, nrow = 4) +
    theme_bw() +
    theme(panel.spacing = unit(0, "lines"),
        axis.title = element_text(color = "black", size = 12, face = "bold"),
        axis.text = element_text(color = "black", size = 12),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        strip.text = element_text(size = 12),
        legend.position = "none"
        )
ggsave(gp, file = "~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/5interactome_specificity_percentage2.pdf", width = 12, height = 10)

# in raw value
## manual create "specific" and "non-specific" categories
count5 <- read.xlsx("~/Documents/INET-work/virus_network/statistic_results/5interactome_specificity_count.xlsx", sheet = 1)
count5_melt <- melt(count5)
count5_melt$data <- factor(count5_melt$data, levels = c("HuSCI", "Gordon", "Li", "Stukalov", "Nabeel"))
count5_melt2 <- aggregate(count5_melt$value, by = list(data = count5_melt$data, variable = count5_melt$variable), FUN = sum)
names(count5_melt2) <- c("data", "variable", "value")

count5_plot <-
    ggplot(count5_melt2, aes(x = data, y = value)) +
    geom_bar(aes(fill = data), position = "dodge", stat = "identity") +
    geom_signif(comparisons = list(c("HuSCI", "Gordon")),
        test = "t.test",
        map_signif_level = TRUE) +
    labs(x = "", y = "# of gene count") +
    facet_wrap(~ variable, nrow = 4) +
    theme_bw() +
    theme(panel.spacing = unit(0, "lines"),
        axis.title = element_text(color = "black", size = 10, face = "bold"),
        axis.text = element_text(color = "black", size = 10),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        strip.text = element_text(size = 6),
        legend.position = "none"
        )
ggsave(count5_plot, file = "~/Documents/INET-work/virus_network/Y2H_screening/20201104_final/figures/5interactome_specificity_rawcount.pdf", width = 14, height = 4)
```

# 9. having tissue specificity based on Dorwie's study
```{r}
dorwie <- c("airway", "brain", "gastrointestinal_tract", "heart", "kidney", "liver", "lung", "muscle", "pancreas")
husci_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% husci_r$from, "dorwie"]))
gordon_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% gordon_r$from, "dorwie"]))
li_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% li_r$from, "dorwie"]))
stukalov_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% stukalov_r$from, "dorwie"]))
nabeel_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% nabeel_r$from, "dorwie"]))
huri_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% huri_tissue$Ensembl_gene_id, "dorwie"]))
bioplex_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% bioplex3_id$Ensembl, "dorwie"]))
bioid_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% bioid1$ensemblID, "dorwie"]))
stgermain_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% bioid_st$ensemblID, "dorwie"]))
sama_dorwie <- as.data.frame(table(has_dorwie[has_dorwie$from %in% bioid_sama$ensemblID, "dorwie"]))

dorward <- list(HuSCI = husci_dorwie,
    Gordon = gordon_dorwie,
    Stukalov = stukalov_dorwie,
    Li = li_dorwie,
    Nabeel = nabeel_dorwie,
    Laurent = bioid_dorwie,
    St_Germain = stgermain_dorwie,
    Samavarchi = sama_dorwie,
    HuRI = huri_dorwie,
    BioPlex3 = bioplex_dorwie,
    HPA = as.data.frame(table(has_dorwie$dorwie))) %>% reduce(full_join, by = "Var1")
colnames(dorward) <- c("tissue", "HuSCI", "Gordon", "Stukalov", "Li", "Nabeel", "Laurent", "St_Germain", "Samavarchi", "HuRI", "BioPlex3", "HPA")
rownames(dorward) <- dorward$tissue
dorward <- dorward[c(1:6, 9, 7, 8), ]
dorward[is.na(dorward)] <- 0
# manual save data in "7interactome_statistics.xlsx, worksheet: inDorward"
dorward <- t(dorward[, c(2:12)]) # worksheet 4
total <- c(length(unique(husci$Ensembl_ID)), length(unique(gordon_science$Ensembl_uniprotIDmapping)), length(unique(stukalov$ensemblID)), length(unique(li$ensemblID)), length(unique(nabeel$Prey_ensembl)), length(unique(bioid1$ensemblID)), length(unique(bioid_st$ensemblID)), length(unique(bioid_sama$ensemblID)), length(unique(c(huri$ensembl_gene_id_a, huri$ensembl_gene_id_b))), length(unique(bioplex3_id$Ensembl)), length(unique(has_all$Ensembl)))
dorward_per <- dorward/total # worksheet 5

df1_melt <- melt(dorward[c(1:8, 11), ])
names(df1_melt) <- c("dataset", "tissue", "value")
df1_melt$tissue <- factor(tolower(df1_melt$tissue), levels = tolower(dorwie))

gp_style <- theme_bw() +
    theme(axis.title = element_text(color = "black", size = 14, face = "bold"),
        axis.text = element_text(color = "black", size = 14),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

gp <- ggplot(df1_melt, aes(x = dataset, y = value)) +
    geom_bar(aes(fill = tissue), stat = "identity", position = "fill") +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(name = "Organ", labels = c("Airway", "Brain", "Gastrointestinal tract", "Heart", "Kidney", "Liver", "Lung", "Muscle", "Pancreas"), values = colorRampPalette(brewer.pal(11,"RdBu"))(9)) +
    labs(x = "", y = "% of gene") +
    gp_style
ggsave(gp, file = "~/Documents/INET-work/virus_network/figure_results/PPI_dorwie_percent.pdf", width = 5, height = 5)
# tissue specific gene in count
df2 <- as.data.frame(t(dorward_per[c(1:8, 11), ]))
df2$tissue <- row.names(df2)
df2_melt <- melt(df2)
df2_melt$tissue <- factor(tolower(df2_melt$tissue), levels = tolower(dorwie))

# library(ggpattern)
#remotes::install_github("coolbutuseless/ggpattern")
ggplot(df2_melt, aes(x = variable, y = value * 100)) +
    geom_bar(aes(fill = variable), stat = "identity") +
    scale_fill_manual(values = colour) +
    labs(x = "", y = "% of gene") +
    facet_wrap(~ tissue, nrow = 3) +
    gp_style +
    theme(strip.background = element_rect(fill = "white")) +
    theme(legend.position = "none")

ggsave(file = "~/Documents/INET-work/virus_network/figure_results/PPI_dorwie_percent_individual_withBioID.pdf", width = 7, height = 7)
```

# 10. fisher test for infected organ
```{r}
pvalue <- c()
for (i in c(2:11)) {
    for (j in c(1:9)) {
        data <- matrix(c(dorward[1, j], dorward[i, j], total[1] - dorward[1, j], total[i] - dorward[i, j]), ncol = 2)
        print(data)
        readline(prompt="Press [enter] to continue")
        ftest <- fisher.test(data)
        print(ftest$p.value)
        pvalue <- c(pvalue, ftest$p.value)
    }
}
padj_value <- p.adjust(pvalue, method = "bonferroni")
pv <- list(
    pvalue = data.frame(matrix(pvalue, ncol = 9, byrow = T)),
    pvalue_bonferroni = data.frame(matrix(padj_value, ncol = 9, byrow = T))
)
names(pv[[1]]) <- names(dorward)
names(pv[[2]]) <- names(dorward)
row.names(pv[[1]]) <- dorward$data[c(2:11)]
row.names(pv[[2]]) <- dorward$data[c(2:11)]
write.xlsx(pv, "~/Documents/INET-work/virus_network/toSummarize/infected_organ/data/pvalue.xlsx", rowNames = T, overwrite = T)
```

# 11. output tissue specificity
```{r}
toOutput <- list(HPA = has_tissue[, c(1:4)],
    HuSCI = unique(merge(husci[, c(1:2)], has_tissue[, c(1:4)], by.x = "Ensembl_ID", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    Gordon = unique(merge(gordon_science[, c(9, 4)], has_tissue[, c(1:4)], by.x = "Ensembl_uniprotIDmapping", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    Stukalov = unique(merge(stukalov[, c(3, 2)], has_tissue[, c(1:4)], by.x = "ensemblID", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    Li = unique(merge(li[, c(5, 2)], has_tissue[, c(1:4)], by.x = "ensemblID", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    Nabeel = unique(merge(nabeel[, c(4, 3)], has_tissue[, c(1:4)], by.x = "Prey_ensembl", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    Laurent = unique(merge(bioid1[, c(4, 2)], has_tissue[, c(1:4)], by.x = "ensemblID", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    St_Germain = unique(merge(bioid_st[, c(3, 2)], has_tissue[, c(1:4)], by.x = "ensemblID", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)],
    Samavarchi = unique(merge(bioid_sama[, c(3, 2)], has_tissue[, c(1:4)], by.x = "ensemblID", by.y = "ensemblID", all.x = TRUE))[, c(1, 2, 4, 5)]
    )

write.xlsx(toOutput, file = "~/Documents/INET-work/virus_network/toSummarize/tissue_specificity/data/tissue_raw.xlsx")
```

# 12. output infected organ
```{r}
toOutput <- list(HPA = has_dorwie,
    HuSCI = has_dorwie[has_dorwie$from %in% husci$Ensembl_ID, ],
    Gordon = has_dorwie[has_dorwie$from %in% gordon_science$Ensembl_uniprotIDmapping, ],
    Stukalov = has_dorwie[has_dorwie$from %in% stukalov$ensemblID, ],
    Li = has_dorwie[has_dorwie$from %in% li$ensemblID, ],
    Nabeel = has_dorwie[has_dorwie$from %in% nabeel$Prey_ensembl, ],
    Laurent = has_dorwie[has_dorwie$from %in% bioid1$ensemblID, ],
    St_Germain = has_dorwie[has_dorwie$from %in% bioid_st$ensemblID, ],
    Samavarchi = has_dorwie[has_dorwie$from %in% bioid_sama$ensemblID, ]
    )
write.xlsx(toOutput, file = "~/Documents/INET-work/virus_network/toSummarize/infected_organ/data/dorard_raw.xlsx")

write.xlsx(dorward, file = "~/Documents/INET-work/virus_network/toSummarize/infected_organ/data/dorward_summary.xlsx")
```
